```{r para-1-background-en, eval = !fr(), results = 'asis'}
cat("# Background

## Description of the Fishery and Management

The commercial fishery for `r sp` has been active for decades. Prior to 2006 there were no limits on the amount of `r sp` that could be caught. In 2006 a Total Allowable Catch (TAC) of 15 kt was established and it remained at this level until 2017. In 2017, the TAC was increased to 17.5 kt and remained there for two years until it was reduced to 14 kt in 2019 as a precautionary measure to address concerns raised by the commercial trawl fleet about their oberved reduction in abundance of Arrowtooth Flounder. In 2020 the TAC was decreased to its current level of 5 kt to address industry concerns regarding declining `r sp` abundance on traditional fishing grounds (@dfomemo2020).

Before the introduction of 100% at-sea observer coverage in the `r bc` groundfish fleets in 1996, reporting of `r sp` discards in fishery logbooks was mandatory, but since `r sp` were not given a TAC until 2005, there was little incentive for skippers to record discards accurately until at-sea observers were present aboard vessels starting in 1996.

Since the `r ca`, there have been two years of new `r sp` commercial catch (2022 and 2023). These values are presented in Table \@ref(tab:fleet-catch-table) and Figure \@ref(fig:fig-catch-fleet). The catch for the Freezer Trawler fleet increased by `r perc_inc_ft_2021_2022`% from 2021 to 2022, but then decreased by `r perc_dec_ft_2022_2023`% from 2022 to 2023. The Shoreside fleet decreased for both years, by `r perc_dec_ss_2021_2022`% from 2021 to 2022, and by `r perc_dec_ss_2022_2023`% from 2022 to 2023.

")
```

```{r para-1-background-fr, eval = fr(), results = 'asis', needs_trans = FALSE}
<<para-1-background-en>>
```

(ref:fig-catch-fleet-en) Commercial catch of `r sp` by fleet and gear type. Each year of catch starts on Feb. 21 and ends on Feb. 20. e.g. the year 2005 catch is all catch between Feb. 21, 2005 to Feb. 20, 2006. The shaded grey area from the beginning of the time series to 1996 indicate unreliable data. In the years prior to 1996, many tows of `r sp` were discarded without logs being kept.

(ref:fig-catch-fleet-fr)  Prises commerciales de `r sp` par flotte et type d'engin. Chaque année de capture commence le 21 février et se termine le 20 février. Par exemple, les captures de l'année 2005 correspondent à toutes les captures effectuées entre le 21 février 2005 et le 20 février 2006. La zone grise du début de la série chronologique jusqu'en 1996 indique que les données ne sont pas fiables. Au cours des années antérieures à 1996, de nombreux traits de `r sp` ont été rejetés sans qu'aucun journal n'ait été tenu.

```{r fig-catch-fleet, fig.cap = ifelse(fr(), "(ref:fig-catch-fleet-fr)", "(ref:fig-catch-fleet-en)")}

yrs <- sort(unique(catch$year))
plot_catch_fleet(list(catch_ft, catch_ss),
                 base_model$dat$fleet_gear_names,
                 french = fr(),
                 unreliable = 1996,
                 xlim = c(min(yrs), max(yrs))) +
  scale_x_continuous(yrs, breaks = seq(min(yrs), yrs[length(yrs)], by = 2)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.55, vjust = 0.5),
        axis.title.x = element_blank())

```

```{r fleet-catch-table, results = "asis"}
cap <- paste0("Recent coastwide commercial fishery landings and discards ",
              "(t) of ", sp, " by fleet.")
if(fr()){
cap <- paste0("Débarquements et rejets (t) récents de la pêche ",
              "commerciale à l'échelle de la côte de ", sp, " par flottille.")
}

table_catch_fleet(list(catch_ft, catch_ss),
                  base_model$dat$fleet_gear_names,
                  digits = 1,
                  caption = cap,
                  start_yr = 1996,
                  font_size = 8,
                  longtable = FALSE,
                  gear_col_widths = "6em")
```
