```{r analysis-and-response-model-en, eval = !fr(), results = 'asis'}
cat("# Analysis and Response

## Stock assessment model

The model used to assess this stock was the Integrated Statistical Catch-at-Age Model (`r iscam`). It was tuned to four fishery-independent trawl survey series covering `r start_catch_yr`--2021, a Discard CPUE series as an index of abundance, annual estimates of commercial catch from two fleets (Freezer Trawlers and Shoreside), and age composition data from the two fleets in the commercial fishery and the four surveys. A two-sex, two-fleet base model was selected and implemented in a Bayesian context using Markov Chain Monte Carlo (MCMC) methods. Leading parameters estimated included $R_0$, initial recruitment, $h$, steepness of the stock-recruitment relationship, $\bar{R}$, average recruitment, and $q_k, k=1,2,3,4,5$, catchability of the four surveys and the Discard CPUE index. Selectivity parameters were also estimated for each sex, fleet, and survey.

Parameter estimates and fixed values are given in Table \@ref(tab:param-estimates-table). As in the `r ca`, the natural mortality was fixed at 0.2 for females and 0.35 for males. Selectivity was estimated for all survey indices but fixed for the Discard CPUE ($a\\hat_7 = 9.5$ and $\\gamma_7 = 0.5$ for both sexes in Table \@ref(tab:param-estimates-table)).

All estimated parameter estimates were very close to those in Table 6 of the `r ca`. The median posterior for $B_0$ decreased from 184.16 in `r ca` to `r f(median(base_model$mcmccalcs$params$sbo), 2)` for this model. The median posterior biomass estimates were also slightly less than the estimates in the `r ca`, so there is almost no scaling effect in the relative biomass and Figure \@ref(fig:fig-base-depletion) looks almost identical to Figure 9 in the `r ca`, other than the two new points for 2022 and 2023. In both cases, relative biomass estimates from 2020 and forward were under the USR $0.4B_0$ reference line.

")
```

```{r analysis-and-response-model-fr, eval = fr(), results = 'asis', needs_trans = TRUE}
<<analysis-and-response-model-en>>
```

```{r analysis-and-response-survey-en, eval = !fr(), results = 'asis'}
cat("## Survey Indices and Catch

In this update, there is one new survey year for each of the three synoptic surveys included in the model (Figure \@ref(fig:fig-base-index-fits)). The `r hsmas` has a terminal year of 2003 and therefore was not updated with any new data. The `r wcviss` took place in 2022; the `r qcsss` and the `r hsss` both took place in 2023. The `r dcpue` had a new index point added for each new year, 2022 and 2023 as it is based on the commercial discards in catch. The `r dcpue` is created using a Generalized Linear Mixed Model (GLMM), and as such all the indices in the time series are estimated each time new data are added anywhere in the time series. The estimated values for each year in the `r dcpue`  (the light grey points and bars in Figure \@ref(fig:fig-base-index-fits)) were therefore slightly different than those in Figure 14 of the `r ca`.

The 2022 point for the `r dcpue` and the 2023 point for the `r qcsss` were not fit well by the model, however the median posterior estimates are within the range of uncertainty for those years. Overall trends of all index estimates follow those seen in the `r ca`, with the `r qcsss` and `r hsss` indices being fit slightly better in the 2005--2012 time period than in the 2022 assessment.

The increase in the survey indices for 2023 is driving the increase in estimated biomass for the beginning of 2024 seen in Figures \@ref(fig:fig-base-sb-bo) and \@ref(fig:fig-base-depletion).
")
```

```{r analysis-and-response-survey-fr, eval = fr(), results = 'asis', needs_trans = TRUE}
<<analysis-and-response-survey-en>>
```

```{r analysis-and-response-loengths-en, eval = !fr(), results = 'asis'}
cat("## Length and Age data

Sex-specific length data have continued to be recorded for the surveys, but have been almost non-existent in the fishery after 2019. Figure \@ref(fig:fig-lengths) shows a summary of the length data; the lack of data since 2019 is evident, except for a small amount in 2019 and moderate amount in 2023 for the Freezer Trawler fleet. Recent survey data show a simliar trend to previous years, with more, and larger, females in the stock. In 2023, the Freezer Trawler fleet saw a larger proportion of smaller males than the large females.

Samples from 2022 and 2023 were not aged for this update, and therefore not included in the update model. Implications of this are discussed in the next section.

Even though there were no new ages added to the update model, age fits and residuals could have changed with the addition of other data. These were double-checked and did not vary at all from the fits and residuals in the `r ca` (Figures 16--26), and therefore are not shown in this update in the interest of keeping the document a reasonable length.
")
```

```{r analysis-and-response-recruitment-en, eval = !fr(), results = 'asis'}
cat("## Recruitment

The posterior median recruitment was estimated to be below the credible interval for the $R_0$ estimate for `r base_model$dat$end.yr - 3`--`r base_model$dat$end.yr`, with a very large credible interval (Figure \@ref(fig:fig-base-recr)). In the `r ca`, only the last two years of recruitment estimates had large credible intervals due to uncertainty around age class strength. The last four years of the model presented here have a large credible interval due to lack of new ages being included in the model for 2022 and 2023. Despite the large uncertainties, the recruitment estimates for `r base_model$dat$end.yr - 3`--`r base_model$dat$end.yr` appear to be slightly increasing and higher than those estimated for 2015--2019.

It is recommended that in addition to catch data and survey indices, the next assessment or update incorporate age data from 2022 to present in the model to alleviate this limitation.
")
```

```{r analysis-and-response-growth-en, eval = !fr(), results = 'asis'}
cat("## Growth

Growth parameters were estimated outside the `r iscam` model and the only differences when compared to the `r ca` were in the scalar in length-weight allometry ($\alpha$) parameter for males which went from $0.0000095$ in the 2022 assessment to $`r base_model$dat$lw.alpha[2]`$, the power in length-weight allometry ($\beta$) parameter for females which went from $3.0515274$ in the 2022 assessment to $`r base_model$dat$lw.beta[1]`$, and the power in length-weight allometry ($\beta$) parameter for males which went from $2.9741834$ in the 2022 assessment to $`r base_model$dat$lw.beta[2]`$. Table \@ref(tab:growth-params-table) shows all the values input into the model for this update, and can be compared directly with Table A.1 in the `r ca` [@arf2022].

")
```

```{r analysis-and-response-fishing-mortality-en, eval = !fr(), results = 'asis'}
cat("## Fishing Mortality and Selectivity

The estimated fishing mortality follows the catch data closely, as this model is tuned to catch. The increase in catch in 2022 in the Freezer Trawler fleet is apparent as is the reduction in catch in 2023 (Figure \@ref(fig:fig-base-f)).

Posterior estimates of age-at-50%-harvest ($\hat{a}_k$) and the standard deviation in the logistic selectivity ogive ($\hat{\gamma}_k$) are provided in Table \@ref(tab:param-estimates-table). The median posterior estimates of those selectivity parameters were similar for males and females for both commercial gears and the surveys. The estimates were all close to the estimates in Table 6 of the `r ca`. There were no drastic changes in the selectivity estimates caused by the addition of new catch and survey index data. The selectivity plots are shown in Figure \@ref(fig:fig-base-mcmc-selex) which when compared to Figure 27 in the `r ca`, shows almost no difference.

")
```

```{r analysis-and-response-growth-fr, eval = fr(), results = 'asis', needs_trans = TRUE}
<<analysis-and-response-growth-en>>
```

```{r analysis-and-response-mcmc-autocorr-en, eval = !fr(), results = 'asis'}
cat("## MCMC Diagnostics

The Markov Chain Monte Carlo (MCMC) chain was run to a length of `r f(mcmc_chain_length)`, with every `r f(mcmc_sample_freq)`^th^ posterior sampled, resulting in `r f(mcmc_num_samples)` posteriors saved. Of those, the first `r f(mcmc_burn_in)` were removed as burn-in, leaving `r f(mcmc_actual_samples)` posteriors used for inference. Those `r f(mcmc_actual_samples)` posteriors were used for all the MCMC diagnostic plots in this update.

Figure \@ref(fig:fig-base-trace) shows the traceplots for the leading parameters, all appear stable as they did in the 2022 assessment. Figure \@ref(fig:fig-base-autocor) shows that there is very little autocorrelation in leading parameters.

The catchability parameters appear to show more correlation with each other in this update model than seen in the `r ca`. A comparison of the pairs plots from this update (Figure \@ref(fig:fig-base-pairs)) and Figure 41 from the `r ca` shows that there is a higher correlation between the $q_1$ and $q_3$ parameters in particular. These are the catchability parameters for the `r qcsss` and the `r hsss`.

")
```

```{r analysis-and-response-mcmc-autocorr-fr, eval = fr(), results = 'asis', needs_trans = TRUE}
<<analysis-and-response-mcmc-autocorr-en>>
```

```{r analysis-and-response-projection-assumptions-en, eval = !fr(), results = 'asis'}
cat("## Projection assumptions

Projection assumptions for this update were identical to those in the `r ca`. Projected log recruitment deviations in the years 2025-2027 were drawn randomly with replacement from the estimated 2010--2019 deviations (omitting poorly estimated 2020--2023 deviations). All other model parameterizations remained the same as in the pre-projection period.
")
```

```{r analysis-and-response-projection-assumptions-fr, eval = fr(), needs_trans = TRUE}
<<analysis-and-response-projection-assumptions-en>>
```

(ref:fig-base-sb-bo-en) Spawning biomass of `r sp` for the base model with $B_0$ reference points. The solid black line with points show the medians of the posteriors, the shaded ribbon encapsulated by dashed lines covers the 95% CI for the posteriors, the point at $B_0$ is the median estimate for the unfished biomass, and the vertical line over that point is the 95% confidence interval.

(ref:fig-base-sb-bo-fr) French here

```{r fig-base-sb-bo, fig.cap = ifelse(fr(), "(ref:fig-base-sb-bo-fr)", "(ref:fig-base-sb-bo-en)")}
plot_biomass_mcmc(base_model,
                  angle_x_labels = TRUE,
                  text_title_size = NULL,
                  show_bo_lines = TRUE,
                  bo_refpt_colors = c("salmon", "darkgreen"),
                  ylim = c(0, 250))
```

(ref:fig-base-depletion-en) Relative spawning biomass for the base model. The shaded area represents the 95% CI. Horizontal lines indicate the 0.2 $B_0$ (solid, red) and 0.4 $B_0$ (dashed, green) reference points. Because the ribbon represents relative spawning biomass (depletion) and the reference points are with respect to $B_0$, all uncertainty about the ratio of the spawning biomass to the reference points is captured in the ribbon and the reference points are shown as point values.

(ref:fig-base-depletion-fr) French here

```{r fig-base-depletion, fig.cap = ifelse(fr(), "(ref:fig-base-depletion-fr)", "(ref:fig-base-depletion-en)")}
plot_biomass_mcmc(base_model,
                  rel = TRUE,
                  show_bo_lines = TRUE,
                  angle_x_labels = TRUE,
                  text_title_size = NULL,
                  ylim = c(0, 1.3))
```

(ref:fig-base-recr-en) Recruitment of `r sp` for the base model. The black points are the medians of the posteriors, the vertical black lines are the 95% CIs for the posteriors, the point at $R_0$ is the median estimate for the initial recruitment parameter $R_0$, and the vertical line over that point and shaded ribbon across the time series is the 95% CI for $R_0$.

(ref:fig-base-recr-fr) Recrutement de `r sp` pour le modèle de base. Les points noirs sont les médianes des valeurs postérieures, les lignes noires verticales sont les IC à 95% des valeurs postérieures, le point à $R_0$ est l'estimation médiane du paramètre de recrutement initial $R_0$, et la ligne verticale au-dessus de ce point et le ruban ombré à travers la série temporelle est l'IC à 95% pour $R_0$.

```{r fig-base-recr, fig.cap = ifelse(fr(), "(ref:fig-base-recr-fr)", "(ref:fig-base-recr-en)")}
plot_recr_mcmc(base_model,
               angle_x_labels = TRUE,
               text_title_size = NULL,
               leg_loc = NULL)
```

(ref:fig-base-index-fits-en) Index fits for the base model. The light grey points and vertical lines show the index values and 95% CIs; the black points show the medians of the posteriors; the black solid vertical lines show the 95% CIs of the posteriors.

<!-- The 2014 WCHG Synoptic index point is shown but was not included in the model. -->

(ref:fig-base-index-fits-fr) Ajustements de l'indice pour le modèle de base. Les points gris clair et les lignes verticales indiquent les valeurs de l'indice et les IC à 95 % ; les points noirs indiquent les médianes des valeurs postérieures ; les lignes verticales pleines noires indiquent les IC à 95 % des valeurs postérieures.

```{r fig-base-index-fits, fig.cap = ifelse(fr(), "(ref:fig-base-index-fits-fr)", "(ref:fig-base-index-fits-en)")}
plot_index_mcmc(base_model,
                type = "fits",
                end_year = 2023,
                surv_index = survey_index,
                leg_loc = NULL,
                text_title_size = NULL)
```

```{r growth-params-table, results = "asis"}
cap <- paste0("Growth parameters estimated outside the ", iscam, " model. All parameters were estimated using samples from the four synoptic surveys, and were filtered to include areas 3CD and 5ABCDE only. For the age-at-50\\% maturity estimates, the following values were used to further filter the data: maturity\\_convention\\_code = 4 (flatfish), maturity\\_code = 5 (Male - Spawning, testes large, white and sperm evident), (Female - Ripe, ovaries containing entirely translucent, mature ova. eggs loose and will run from oviducts under slight pressure), and usability codes = 0 (Unknown), 1 (Fully usable), 2 (Fail, but all data usable), 6 (Gear torn, all data ok).")
if(fr()){
  cap <- paste0("Paramètres de croissance estimés en dehors du modèle ", iscam, ". Tous les paramètres ont été estimés à l'aide d'échantillons provenant des quatre campagnes synoptiques, et ont été filtrés pour inclure uniquement les zones 3CD et 5ABCDE. Pour les estimations de l'âge à 50 ans et de la maturité, les valeurs suivantes ont été utilisées pour filtrer davantage les données : code de maturité = 4 (poissons plats), code de maturité = 5 (mâle - frai, testicules larges, blancs et sperme évident), (femelle - mûre, ovaires contenant des ovules entièrement translucides et matures. Les œufs se détachent et s'écoulent des oviductes sous une légère pression), et les codes d'utilisabilité = 0 (Inconnu), 1 (Entièrement utilisable), 2 (Échec, mais toutes les données sont utilisables), 6 (Équipement déchiré, toutes les données sont correctes).")
}

table_growth_params(base_model,
                    digits = 3,
                    alpha_digits = 7,
                    caption = cap)

```

```{r param-estimates-table, results = "asis"}
cap <- paste0("Posterior median and 95\\% credible interval estimates of key ",
              "parameters for the base model.")
if(fr()){
cap <- paste0("Estimations de la médiane postérieure et de l'intervalle ",
              "crédible à 95 \\% des paramètres clés pour le modèle de base.")
}

table_param_est_mcmc(base_model,
                     font_size = 8,
                     caption = cap,
                     bold_header = FALSE,
                     show_year_range = FALSE)
```

(ref:fig-lengths-en) Length-frequency plot where female fish are shown as red bars and male fish are shown behind as blue bars. The total number of fish measured for a given survey or fishery per year are indicated in the top left corner of each panel. Histograms are only shown if there are more than 20 fish measured for a given survey-year combination. 

(ref:fig-lengths-fr) French here

```{r fig-lengths, fig.cap = ifelse(fr(), "(ref:fig-lengths-fr)", "(ref:fig-lengths-en)"), fig.asp = 1, out.width = "6in"}

bin_width1 <- diff(quantile(length_samples_survey$length,
  na.rm = TRUE,
  probs = c(0, 1)
)) / 20

bin_width2 <- diff(quantile(length_samples_ft$length,
  na.rm = TRUE, probs = c(0, 1)
)) / 20

bin_width3 <- diff(quantile(length_samples_ss$length,
  na.rm = TRUE, probs = c(0, 1)
)) / 20

bin_width <- mean(c(bin_width1, bin_width2, bin_width3), na.rm = TRUE)

ss <- tidy_lengths_weighted(length_samples_survey,
                            dat_survey_sets = dat$survey_sets,
                            bin_size = bin_width,
                            sample_type = "survey")

sf <- length_samples_ft |> 
  # mutate(sex = 2) %>% # fake all sex as female for commercial samples; often not sexed
  tidy_lengths_weighted(dat_catch = dat$catch,
                        bin_size = bin_width,
                        sample_type = "commercial", spp_cat_code = 1) |> 
  mutate(survey_abbrev = tr("Freezer Trawlers"))

sc <- length_samples_ss |> 
  # mutate(sex = 2) %>% # fake all sex as female for commercial samples;
  # often not sexed
  tidy_lengths_weighted(dat_catch = dat$catch,
                        bin_size = bin_width,
                        sample_type = "commercial", spp_cat_code = 1) |> 
  mutate(survey_abbrev = tr("Shoreside"))

min_total <- 20
 # are we interested in length frequencies pre-1980?
sc_old <- filter(sc, year < 1995)
sc <- filter(sc, year > 1995)
sb <- bind_rows(ss, sc, sf) |> 
  mutate(survey_abbrev = tr(survey_abbrev, allow_missing = TRUE)) |> 
  mutate(survey_abbrev = factor(survey_abbrev)) |> 
  mutate(year = factor(year))

g_lengths <- plot_lengths(sb,
                          fill_col = c("M" = "#0096FF10", "F" = "#FF000010"),
                          line_col = c("M" = "#0000FF", "F" = "#FF0000"),
                          survey_cols = NULL,
                          bin_size = bin_width,
                          min_total = min_total,
                          french = fr()) +
  # scale_x_continuous(breaks = x_breaks, labels = x_labels) +
  guides(colour = "none", fill = "none") +
  ggtitle("") +
  xlab(paste(tr("Length"), "(cm)")) +
  ylab(tr("Relative length frequency"))

g_lengths
```

(ref:fig-base-f-en) Fishing mortality for the base model for the two trawl fisheries for females only. The plots for the males are not shown, because they are the same. The shaded area represents the 95% CI.

(ref:fig-base-f-fr) French here

```{r fig-base-f, fig.cap = ifelse(fr(), "(ref:fig-base-f-fr)", "(ref:fig-base-f-en)")}
plot_f_mcmc(base_model,
            angle_x_labels = TRUE,
            text_title_size = NULL, xlim = c(1997, 2023))
```

(ref:fig-base-selex-en) Estimated and fixed selectivities by sex for the base model. The dots show estimated median selectivity-at-age, and the shaded areas show the 95% credible intervals (CI). Single dotted lines with no CI (HS Multi, Discard CPUE) represent fixed selectivities. Dashed lines represent maturity-at-age based on logistic curves fit to the proportion of mature fish at age.

(ref:fig-base-selex-fr) Sélectivités estimées et fixées par sexe pour le modèle de base. Les points indiquent la sélectivité médiane estimée à l'âge, et les zones ombrées indiquent les intervalles de crédibilité (IC) à 95 %. Les lignes pointillées simples sans IC (HS Multi, Discard CPUE) représentent les sélectivités fixes. Les lignes en pointillé représentent la maturité à l'âge sur la base de courbes logistiques ajustées à la proportion de poissons matures à l'âge.

```{r fig-base-mcmc-selex, fig.cap = ifelse(fr(), "(ref:fig-base-selex-fr)", "(ref:fig-base-selex-en)")}
plot_selex_mcmc(base_model,
                show_maturity = TRUE,
                leg_loc = "facet")
```

(ref:fig-base-trace-en) Trace plots for MCMC output of estimated lead parameters in the base model. The MCMC run has chain length `r f(mcmc_chain_length)` with a sample taken every `r f(mcmc_sample_freq)`^th^ iteration. Of the `r f(mcmc_num_samples)` samples taken, the first `r f(mcmc_burn_in)` were removed as a burn-in period. Numerical indices on Catchability ($q$) parameters for the survey indices are defined as: `r paste(base_index_gears$gear, " = ", base_index_gears$gear_name, collapse = ", ")`.

(ref:fig-base-trace-fr) French here

```{r fig-base-trace, fig.cap = ifelse(fr(), "(ref:fig-base-trace-fr)", "(ref:fig-base-trace-en)"), fig.asp = 1}
plot_traces_mcmc(base_model,
                 plot_sel = FALSE, 
                 param_rm = c("m1", "m2", "rho", "ssb", "vartheta",
                              "bo", "msy1", "msy2", "fmsy1", "fmsy2",
                              "umsy1", "umsy2","bmsy",
                              "so", "beta", "phie"),
                 text_title_size = NULL)
```

(ref:fig-base-autocor-en) Autocorrelation plots for MCMC output of estimated lead parameters in the base model. The x-axis values are the lag between posteriors. Numerical indices on Catchability ($q$) parameters for the survey indices are defined as: `r paste(base_index_gears$gear, " = ", base_index_gears$gear_name, collapse = ", ")`. 

(ref:fig-base-autocor-fr) French here

```{r fig-base-autocor, fig.cap = ifelse(fr(), "(ref:fig-base-autocor-fr)", "(ref:fig-base-autocor-en)"), fig.asp = 1}
plot_autocorr_mcmc(base_model,
                   plot_sel = FALSE, 
                   param_rm = c("m1", "m2", "rho", "ssb", "vartheta",
                                "bo", "msy1", "msy2", "fmsy1", "fmsy2",
                                "umsy1", "umsy2","bmsy",
                                "so", "beta", "phie"),
                   rows_cols = c(3, 4),
                   text_title_size = NULL,
                   lag_max = 100,
                   col = "blue",
                   lwd = 2)
```

(ref:fig-base-pairs-en) Pairs plots for MCMC estimated parameters in the base model. The lines in the points plots in the lower triangular panels are linear models with shaded 95% confidence intervals. The line plots in the diagonal panels represent density of the parameter values, and the values in the upper triangular panels are the correlations between parameters with text size being directly proportional to the absolute value of those values. Numerical indices on Catchability ($q$) parameters for the survey indices are defined as: `r paste(base_index_gears$gear, " = ", base_index_gears$gear_name, collapse = ", ")`.

(ref:fig-base-pairs-fr) French here

```{r fig-base-pairs, fig.cap = ifelse(fr(), "(ref:fig-base-pairs-fr)", "(ref:fig-base-pairs-en)"), fig.asp = 1}

plot_pairs_mcmc(base_model,
                plot_sel = FALSE,
                param_rm = c("m1", "m2", "rho", "ssb",
                             "msy1", "msy2",
                             "fmsy1", "fmsy2",
                             "umsy1", "umsy2",
                             "bmsy", "bo", "sbo", "vartheta",
                             "so", "beta", "phie"),
                text_title_size = NULL,
                tick_label_size = 4,
                point_size = 0.5)
```

\clearpage

```{r indicators-of-stock-status-en, eval = !fr(), results = 'asis'}
cat("## Indicators of Stock Status

Typically DFO's reference points of $0.4B_{MSY}$ for the LRP and $0.8B_{MSY}$ for the USR are used as they are defined in the Sustainable Fisheries Framework (SFF, [@dfo2009]). However for `r sp`, reference points based on the Maximum Sustainable Yield (MSY) were strongly impacted by estimates of selectivity in the trawl fisheries. Because the selectivity ogives were estimated to the right of the maturity ogive, the MSY-based reference points were overly optimistic, since the vulnerable biomass appeared to include the entire stock, and not just the mature fish. Reference points based on estimated equilibrium unfished spawning biomass, $B_0$, were used instead as $B_0$ is not impacted directly by selectivity estimates. Because the reference points used here are not the standard SFF reference points, the typical stock 'zones' (i.e. healthy, cautious, and critical) are not defined.

Projection of catch levels was performed for this update, but the values were truncated in comparison to the `r ca`. Advice was given to Science from Fisheries managers that the projected catch levels should be from 1 to 8 kilotonnes (kt) in increments of 1 kt for this update instead of 1 to 15 kt as was applied in the `r ca`. Figure \@ref(fig:fig-rel-biomass-proj) shows the biomass trajectories resulting in the application of the catch levels as catch to the stock for the years `r end_yr + 2`--`r end_yr + base_model$proj$num.projyrs + 1`. Figure \@ref(fig:fig-rel-biomass-proj-closeup) shows a closer view of the projected trajectories.

Harvest decision tables are provided as advice to managers (Tables \@ref(tab:decision-table-02bo)--\@ref(tab:decision-table-decreasing-biomass)) with constant catch policies ranging from 1 to 8 kilotonnes, from `r base_model$dat$end.yr + 2` to `r base_model$dat$end.yr +  base_model$proj$num.projyrs + 1`. To interpret the decision tables with respect to the LPR ($0.2B_0$) and USR ($0.4B_0$), the probability of being above the USR is $P(B_t > USR)$, the probability of being above the LRP but below the USR is $P(B_t > LRP) - P(B_t > USR)$, and the probability of being below the LRP is $1 - P(B_t > LRP)$, where $t$ is the year, and $B_t$ is the relative biomass at the beginning of year $t$.

During the review meeting for the `r ca`, participants deliberated about the validity of the USR being set to $0.4B_0$ and requested an 'alternative USR' of $0.35B_0$. This was included in the 2022 Research Document and is included in this update as well.

Harvest decision tables provided in this document include probabilities at the beginning of the year of being above:

1. the LRP of $02.B_0$ (Table \@ref(tab:decision-table-02bo)),
2. the alternative USR of $0.35B_0$ (Table \@ref(tab:decision-table-035bo)), and
3. the USR of $0.4B_0$ (Table \@ref(tab:decision-table-04bo)),
4. the previous year's biomass (Table \@ref(tab:decision-table-decreasing-biomass))

Figures \@ref(fig:fig-catch-streams-nextyr-proj)--\@ref(fig:fig-catch-streams-nextnextnextyr-proj) show the uncertainty in the relative spawning biomass estimates for projected years given the catch values provided in the harvest decision tables. They are essentially a visual depiction of the decision tables, except that the lower 2.5% and upper 2.5% of the posteriors are not included in the plots, but are included in the probability calculations in the decision tables. The horizontal lines in the figures are the 95% CIs of the relative biomass. The probabilities given in the harvest decision tables are close to being the proportion of those lines to the right of each reference point shown as vertical lines in the plots.

")
```

```{r indicators-of-stock-status-fr, eval = fr(), results = 'asis', needs_trans = TRUE}
<<indicators-of-stock-status-en>>
```

(ref:fig-rel-biomass-proj-en) Estimated relative spawning biomass ($B_t/B_0$) for the base model. The shaded area represents the 95% Credible Interval (CI) and the solid line with points shows the connected medians. Horizontal lines indicate the $0.2B_0$ (solid red) and $0.4B_0$ (dashed green) reference points. The colored dots from `r end_yr + 2`--`r end_yr + base_model$proj$num.projyrs + 1` are the posterior medians representing the projected catch levels, with solid lines connecting them; the dashed lines from `r end_yr + 2`--`r end_yr + base_model$proj$num.projyrs + 1` represent the 95% CIs for those posteriors. The constant catch values (in kt) are shown as text on the right of the end points of each projected trajectory. See the decision tables (Tables \@ref(tab:decision-table-02bo)--\@ref(tab:decision-table-decreasing-biomass)) for probabilities of being above reference points and of the stock increasing year-to-year in the projection years for each catch level.

(ref:fig-rel-biomass-proj-fr) French here

```{r fig-rel-biomass-proj, fig.cap = ifelse(fr(), "(ref:fig-rel-biomass-proj-fr)", "(ref:fig-rel-biomass-proj-en)")}
plot_biomass_proj_mcmc(base_model,
                       palette = "Spectral",
                       leg_loc = NULL,
                       rel = TRUE,
                       xlim = c(1997, 2027),
                       ylim = c(0, 1.2),
                       show_bo_lines = TRUE,
                       angle_x_labels = TRUE,
                       line_width = 0.5,
                       point_size = 1,
                       label_font_size = 3,
                       proj_catch_vals = 1:8)
```

(ref:fig-rel-biomass-proj-closeup-en) Closeup view of most recent relative spawning biomass (Figure \@ref(fig:fig-rel-biomass-proj)) for the `r sp` base model with $B_0$-based reference points and projections into the future. The constant catch values (in kt) are shown as text on the right of the end points of each projected trajectory. See the decision tables (Tables \@ref(tab:decision-table-02bo)--\@ref(tab:decision-table-decreasing-biomass)) for probabilities of being above reference points and of the stock increasing year-to-year in the projection years for each catch level.

(ref:fig-rel-biomass-proj-closeup-fr) French here

```{r fig-rel-biomass-proj-closeup, fig.cap = ifelse(fr(), "(ref:fig-rel-biomass-proj-closeup-fr)", "(ref:fig-rel-biomass-proj-closeup-en)")}
plot_biomass_proj_mcmc(base_model,
                       palette = "Spectral",
                       leg_loc = NULL,
                       rel = TRUE,
                       xlim = c(2020, 2027),
                       ylim = c(0, 0.9),
                       show_bo_lines = TRUE,
                       angle_x_labels = TRUE,
                       line_width = 0.5,
                       point_size = 1,
                       label_font_size = 3,
                       nudge_catch_labels = c(-0.1, 0),
                       proj_catch_vals = 1:8)
```

(ref:fig-catch-streams-proj-nextyr-en) Projected `r base_model$dat$end.yr + 2` relative spawning biomass for several possible catch levels in `r base_model$dat$end.yr + 1`. Black points are medians of the posterior and horizontal black lines are the 95% CI (2.5%--97.5%). The solid red line is the LRP, $0.2B_0$, the dotted blue line is the alternative USR, $0.35B_0$, and the dashed green line is the USR, $0.4B_0$.

(ref:fig-catch-streams-proj-nextyr-fr) French here

```{r fig-catch-streams-nextyr-proj, fig.cap = ifelse(fr(), "(ref:fig-catch-streams-proj-nextyr-fr)", "(ref:fig-catch-streams-proj-nextyr-en)")}

plot_ref_points_dist_mcmc(base_model,
                          biomass_col = "B2025",
                          proj_catch_vals = 1:8)
```
(ref:fig-catch-streams-proj-nextnextyr-en) Projected `r base_model$dat$end.yr + 3` relative spawning biomass for several possible catch levels in `r base_model$dat$end.yr + 2`. Black points are medians of the posterior and horizontal black lines are the 95% CI (2.5%--97.5%). The solid red line is the LRP, $0.2B_0$, the dotted blue line is the alternative USR, $0.35B_0$, and the dashed green line is the USR, $0.4B_0$.

(ref:fig-catch-streams-proj-nextnextyr-fr) French here.

```{r fig-catch-streams-nextnextyr-proj, fig.cap = ifelse(fr(), "(ref:fig-catch-streams-proj-nextnextyr-fr)", "(ref:fig-catch-streams-proj-nextnextyr-en)")}

plot_ref_points_dist_mcmc(base_model,
                          biomass_col = "B2026",
                          proj_catch_vals = 1:8)
```

(ref:fig-catch-streams-proj-nextnextnextyr-en) Projected `r base_model$dat$end.yr + 4` relative spawning biomass for several possible catch levels in `r base_model$dat$end.yr + 3`. Black points are medians of the posterior and horizontal black lines are the 95% CI (2.5%--97.5%). The solid red line is the LRP, $0.2B_0$, the dotted blue line is the alternative USR, $0.35B_0$, and the dashed green line is the USR, $0.4B_0$.

(ref:fig-catch-streams-proj-nextnextnextyr-fr) French here.

```{r fig-catch-streams-nextnextnextyr-proj, fig.cap = ifelse(fr(), "(ref:fig-catch-streams-proj-nextnextnextyr-fr)", "(ref:fig-catch-streams-proj-nextnextnextyr-en)")}

plot_ref_points_dist_mcmc(base_model,
                          biomass_col = "B2027",
                          proj_catch_vals = 1:8)
```

```{r decision-table-02bo, results = "asis"}

cap <- paste0("Probabilities that projected biomass will be above the $0.2B_0$ LRP for catch levels of 1 to 8 kt.")

if(fr()){
  cap <- "Probabilités que la biomasse projetée soit supérieure au PRL de $0,2B_0$ pour des niveaux de capture de 1 à 8 kt."
}
table_decision(base_model,
               catch_vals = 1:8,
               rm_yrs = 2024,
               refpt = 0.2,
               prob_gt = TRUE,
               year_to_year = FALSE,
               cap = cap)
```

```{r decision-table-035bo, results = "asis"}

cap <- paste0("Probabilities that projected biomass will be above the $0.35B_0$ alternative USR for catch levels of 1 to 8 kt.")

if(fr()){
  cap <- "Probabilités que la biomasse projetée soit supérieure au USR alternatif de $0,35B_0$ pour des niveaux de capture de 1 à 8 kt."
}
table_decision(base_model,
               catch_vals = 1:8,
               rm_yrs = 2024,
               refpt = 0.35,
               prob_gt = TRUE,
               year_to_year = FALSE,
               cap = cap)
```

```{r decision-table-04bo, results = "asis"}

cap <- paste0("Probabilities that projected biomass will be above the $0.4B_0$ USR for catch levels of 1 to 8 kt.")

if(fr()){
  cap <- "Probabilités que la biomasse projetée soit supérieure au USR de $0,4B_0$ pour des niveaux de capture de 1 à 8 kt."
}
table_decision(base_model,
               catch_vals = 1:8,
               rm_yrs = 2024,
               refpt = 0.4,
               inc_years = -2024,
               prob_gt = TRUE,
               year_to_year = FALSE,
               cap = cap)
```

```{r decision-table-decreasing-biomass, results = "asis"}

cap <- paste0("Probabilities that projected biomass will increase for catch levels of 1 to 8 kt.")

if(fr()){
  cap <- "Probabilités que la biomasse projetée augmente pour des niveaux de capture de 1 à 8 kt. "
}
table_decision(base_model,
               catch_vals = 1:8,
               prob_gt = TRUE,
               year_to_year = TRUE,
               cap = cap)
```
