# Bridging analysis

The base model from the 2015 assessment was run with the newest version of the iSCAM code and the original data files and the results were determined to be identical.

Various modifications were made incrementally to the 2015 base model to create a set of bridging models which evaluate the component-specific effects of all changes from the 2015 base model to the 2021 base model.

As a reminder, the 2015 base model was a female-only catch-at-age model with 4 indices of abundance which included the three Synoptic surveys and the Hecate Strait Multispecies assemblage survey.

The bridging models were constructed in several steps and are compared in the following subsections.

## Single-fleet female only models

The models in this section were produced as follows. Each model is a copy of the previous one with only one change made so incremental changes can be easily tracked.


1. Extracted the data used in the 2015 model using the **gfplot** package, which has been used in several assessments and in the **gfsynopsis** report. Ran the 2015 model without any modifications other than this data change.

1. Using the same data extraction methods as in the first step, appended data up to and including 2019.

1. Attempted to add the West Coast Haida Gwaii Synoptic survey (WCHGSS) but the model fails to estimate trawl selectivity when both the Hecate Strait Multispecies Assemblage survey (HSMAS) and the WCHGSS are included, so the WCHGSS was left out due to its limited area and years of coverage and because the HSMAS covers the early period of the time series.

1. Added the Discard CPUE index. This was suggested by the Technical Working Group (TWG) and is an index for vessels that were not fishing for `r sp` and therefore were discarding all that they caught incidentally. The selectivity could not reliably be estimated for this index in the current model configuration, so its selectivity was set to mirror that of the trawl fishery (Table \@ref(tab:bridge1-sel-param-table)). This decision was based on the Discard CPUE being directly extracted from the trawl fishery data. The Discard CPUE index is described in greater detail in later sections.

(ref:fig-bridge1-biomass) Maximum Posterior Density (MPD) estimates of spawning biomass (top panel) and relative spawning biomass (bottom panel) for the 2015 base model and models with cumulative changes to that model including data changes and additions, and the addition of the Discard CPUE index.

(ref:fig-bridge1-biomass-french) French caption here

```{r bridge1-biomass, fig.cap = ifelse(french, "(ref:fig-bridge1-biomass-french)", "(ref:fig-bridge1-biomass)"), out.width = "100%" , fig.pos="H"}
cowplot::plot_grid(plot_ts_mpd(models$bridge_models[[1]], type = "sbt", legend_title = "Bridge models - 1 fleet, 1 sex"),
                   plot_ts_mpd(models$bridge_models[[1]], type = "sbt", rel = TRUE, legend_title = "Bridge models - 1 fleet, 1 sex") + 
                     coord_cartesian(ylim = c(0, 1)), nrow = 2)
                   
```

(ref:fig-bridge1-recruitment) Maximum Posterior Density (MPD) estimates of recruitment for the 2015 base model and models with cumulative changes to that model including data changes and additions, and the addition of the Discard CPUE index.

(ref:fig-bridge1-recruitment-french) French caption here

```{r bridge1-recruitment, fig.cap = ifelse(french, "(ref:fig-bridge1-recruitment-french)", "(ref:fig-bridge1-recruitment)"), out.width = "100%" , fig.pos="H"}
plot_ts_mpd(models$bridge_models[[1]], type = "rt", legend_title = "Bridge models - 1 fleet, 1 sex") +
  coord_cartesian(ylim = c(0, 1.5))
```

(ref:fig-bridge1-index-fits) Maximum Posterior Density (MPD) index fits for the 2015 base model and models with cumulative changes to that model including data changes and additions, and the addition of the Discard CPUE index.

(ref:fig-bridge1-index-fits-french) French caption here

```{r bridge1-index-fits, fig.cap = ifelse(french, "(ref:fig-bridge1-index-fits-french)", "(ref:fig-bridge1-index-fits)"), out.width = "100%" , fig.pos="H"}
plot_index_fit_mpd(models$bridge_models[[1]], surv_index = survey_index, legend_title = "Bridge models - 1 fleet, 1 sex")
```

(ref:fig-bridge1-selectivities) Maximum Posterior Density (MPD) maturity ogives and selectivity estimates for all gears in the models with one fleets and one sex. The dashed blue and red lines are the male and female maturity ogives respectively, the blue and red lines with points are the yearly selectivity estimates for males and females respectively.

```{r bridge1-selectivities, fig.cap = "(ref:fig-bridge1-selectivities)"}
library(gridExtra)
plist <- map2(models$bridge_models[[1]], names(models$bridge_models[[1]]), ~{
  plot_selex(.x, show_maturity = TRUE, title = .y) +
    theme(plot.title = element_text(face = "bold", size = 12),
          axis.text.x = element_text(size = 6),
          strip.text.x = element_text(size = 6))
})
n <- length(plist)
nrow <- floor(sqrt(n))
do.call("grid.arrange", c(plist, nrow = nrow))
```

\clearpage

```{r bridge1-param-settings-table, results = 'asis'}
param_settings_table(
  models$bridge_models[[1]][[1]],
  format = "latex",
  font_size = 7,
  caption = ifelse(
    french,
    "French goes here",
    "Number of parameters estimated, bounds, and prior parameterizations for the model '2015 Base model'."))
```

```{r bridge1-param-table, results = 'asis'}
param_est_mpd_table(
  models$bridge_models[[1]],
  format = "latex",
  digits = 3,
  font_size = 7,
  model_col_widths = "5em",
  caption = ifelse(
    french,
    "French goes here",
    "Bridge model parameter estimates for the primary parameters, reference points, and catchability estimates ($q$) for each index.")) 
```

```{r bridge1-sel-param-table, results = 'asis'}
sel_param_est_mpd_table(
  models$bridge_models[[1]],
  format = "latex",
  digits = 3,
  font_size = 7,
  model_col_widths = "5em",
  caption = ifelse(
    french,
    "French goes here",
    "A comparison of Bridge model selectivity parameter estimates. The number in parentheses in the 'Type' column represents the iSCAM code for the type of selectivity used. For example, a Logistic selectivity can have type '1' or '6'. The '6' allows for fixing the selectivity parameters. In the 'Fixed' column all blank entries are estimated parameters, fixed parameters are labelled 'Yes', and selectivities mirrored to another gear, which has been estimated are labelled as such. Dashes are not applicable parameters for that model."))  %>% 
  column_spec(1, width = "8em")
```
\clearpage

## Single-fleet splix-sex models

The models in this section have only one change made with respect to the previous model so incremental changes can be tracked. The starting model in this section (*Add Discard CPUE*) is repeated from Section \@ref(single-fleet-female-only-models) so that relative differences in trends can be seen.

1. Converted the model to have a split-sex age structure. The TWG agreed that calculation of proportions female to be multiplied by catch values was not statistically robust enough and that given the sexual dimorphism of the species a split-sex model should be used. As was the case in the single-fleet, single-sex models, the selectivity could not be reliably estimated for the WCVISS index, so its selectivity was set to mirror that of the HSSS index (Table \@ref(tab:bridge2-sel-param-table)).

1. Changed the fishing year to be from January 1 - December 31 to the current management period which is Feb. 21 - Feb. 20. All catch and commercial age-compositions were modified and re-weighted.

1. Fixed male Natural mortality to be 0.2, and female to be 0.35. These are the values that are used in the Gulf of Alaska assessment.

<!-- 1. Fixed both male and female Natural mortality to be 0.2 to examine the effects on estimates of other parameters. -->

(ref:fig-bridge2-biomass) Maximum Posterior Density (MPD) estimates of spawning biomass (top panel) and relative spawning biomass (bottom panel) for the single sex *Add Discard CPUE* model and models based on it but changed to split-sex.

(ref:fig-bridge2-biomass-french) French caption here

```{r bridge2-biomass, fig.cap = ifelse(french, "(ref:fig-bridge2-biomass-french)", "(ref:fig-bridge2-biomass)"), out.width = "100%" , fig.pos="H"}
cowplot::plot_grid(
  plot_ts_mpd(models$bridge_models[[2]],
              type = "sbt",
              legend_title = "Bridge models - 1 fleet, 2 sexes"),
  plot_ts_mpd(models$bridge_models[[2]],
              type = "sbt",
              rel = TRUE, 
              legend_title = "Bridge models - 1 fleet, 2 sexes") + 
    coord_cartesian(ylim = c(0, 1)), nrow = 2)
```

(ref:fig-bridge2-recruitment) Maximum Posterior Density (MPD) estimates of recruitment for the single sex 'Add Discard CPUE' model and models base on it but changed to split-sex.

(ref:fig-bridge2-recruitment-french) French caption here

```{r bridge2-recruitment, fig.cap = ifelse(french, "(ref:fig-bridge2-recruitment-french)", "(ref:fig-bridge2-recruitment)"), out.width = "100%" , fig.pos="H"}
plot_ts_mpd(models$bridge_models[[2]],
            type = "rt",
            legend_title = "Bridge models - 1 fleet, 2 sexes") +
  coord_cartesian(ylim = c(0, 0.4))
```

(ref:fig-bridge2-index-fits) Maximum Posterior Density (MPD) index fits for the single sex 'Add Discard CPUE' model and models base on it but changed to split-sex.

(ref:fig-bridge2-index-fits-french) French caption here

```{r bridge2-index-fits, fig.cap = ifelse(french, "(ref:fig-bridge2-index-fits-french)", "(ref:fig-bridge2-index-fits)"), out.width = "100%" , fig.pos="H"}
plot_index_fit_mpd(
  models$bridge_models[[2]],
  surv_index = survey_index,
  point_size = 1, legend_title = "Bridge models - 1 fleet, 2 sexes")
```

(ref:fig-bridge2-selectivities) Maximum Posterior Density (MPD) maturity ogives and selectivity estimates for all gears in the models with one fleet and two sexes. The dashed blue and red lines are the male and female maturity ogives respectively, the blue and red lines with points are the yearly selectivity estimates for males and females respectively.

```{r bridge2-selectivities, fig.cap = "(ref:fig-bridge2-selectivities)"}
plist <- map2(models$bridge_models[[2]], names(models$bridge_models[[2]]), ~{
  plot_selex(.x, show_maturity = TRUE, title = .y) +
    theme(plot.title = element_text(face = "bold", size = 12),
          axis.text.x = element_text(size = 6),
          strip.text.x = element_text(size = 6))
})
n <- length(plist)
nrow <- floor(sqrt(n))
do.call("grid.arrange", c(plist, nrow = nrow))
```

(ref:fig-bridge2-age-fit-1) Maximum Posterior Density (MPD) age comp fits for the 'Change fishing year to Feb 21 - Feb 20' model, for the 'COMM' gear.

```{r bridge2-agefit-1, fig.cap = "(ref:fig-bridge2-age-fit-1)", fig.asp = 1.4}
plot_agecomp_fits_splitsex(models$bridge_models[[2]][[3]], 1)
```

(ref:fig-bridge2-age-fit-2) Maximum Posterior Density (MPD) age comp fits for the 'Change fishing year to Feb 21 - Feb 20' model, for the 'SYN QCS' gear.

```{r bridge2-agefit-2, fig.cap = "(ref:fig-bridge2-age-fit-2)"}
plot_agecomp_fits_splitsex(models$bridge_models[[2]][[3]], 2)
```

(ref:fig-bridge2-age-fit-4) Maximum Posterior Density (MPD) age comp fits for the 'Change fishing year to Feb 21 - Feb 20' model, for the 'SYN HS' gear.

```{r bridge2-agefit-4, fig.cap = "(ref:fig-bridge2-age-fit-4)"}
plot_agecomp_fits_splitsex(models$bridge_models[[2]][[3]], 3)
```
(ref:fig-bridge2-age-fit-5) Maximum Posterior Density (MPD) age comp fits for the 'Change fishing year to Feb 21 - Feb 20' model, for the 'SYN WCVI' gear.

```{r bridge2-agefit-5, fig.cap = "(ref:fig-bridge2-age-fit-5)"}
plot_agecomp_fits_splitsex(models$bridge_models[[2]][[3]], 4)
```

\clearpage

```{r bridge2-param-settings-table, results = 'asis'}
param_settings_table(
  models$bridge_models[[2]][[2]],
  format = "latex",
  font_size = 7,
  caption = ifelse(
    french,
    "French goes here",
    "Number of parameters estimated, bounds, and prior parameterizations for the single-fleet model 'Convert to split-sex'."))
```

```{r bridge2-param-table, results = 'asis'}
param_est_mpd_table(
  models$bridge_models[[2]],
  format = "latex",
  digits = 3,
  font_size = 7,
  model_col_widths = "5em",
  caption = ifelse(
    french,
    "French goes here",
    "Bridge model parameter estimates for the primary parameters, reference points, and catchability estimates ($q$) for each index for the models with a single fleet and two sexes.")) 
```

```{r bridge2-sel-param-table, results = 'asis'}
sel_param_est_mpd_table(
  models$bridge_models[[2]],
  format = "latex",
  digits = 3,
  font_size = 7,
  model_col_widths = "5em",
  caption = ifelse(
    french,
    "French goes here",
    "A comparison of Bridge model selectivity parameter estimates for the single-fleet, two-sex models."))  %>% 
  column_spec(1, width = "8em")
```
\clearpage

## Two-fleet Single-sex models

Each model in this section is based on the previous one with only one change made so incremental changes can be tracked. The starting model here (*Update data to 2021*) is repeated from Section \@ref(single-fleet-female-only-models) so that relative differences in trends can be seen.

1. Modified the model to have two commercial fishing fleets. The two fleets represented are the Freezer trawlers which freeze their catch at sea and the wet boats which typically make one trawl of `r sp` at the end of trips which target other species in an effort to minimize the effects of proteolysis on the flesh.

1. Added the Discard CPUE index. The addition of this index was the same method as in the single-sex model (Section \@ref(single-fleet-female-only-models)).

(ref:fig-bridge3-biomass) Maximum Posterior Density (MPD) estimates of spawning biomass (top panel) and relative spawning biomass (bottom panel) for the 'Update data to 2021' and female-only models with two fleets.

(ref:fig-bridge3-biomass-french) French caption here

```{r bridge3-biomass, fig.cap = ifelse(french, "(ref:fig-bridge3-biomass-french)", "(ref:fig-bridge3-biomass)"), out.width = "100%" , fig.pos="H"}
cowplot::plot_grid(
  plot_ts_mpd(models$bridge_models[[3]],
              type = "sbt",
              legend_title = "Bridge models - 2 fleets, 1 sex"),
  plot_ts_mpd(models$bridge_models[[3]],
              type = "sbt",
              rel = TRUE,
              legend_title = "Bridge models - 2 fleets, 1 sex") + 
    coord_cartesian(ylim = c(0, 1)), nrow = 2)
```

(ref:fig-bridge3-recruitment) Maximum Posterior Density (MPD) estimates of recruitment for the 'Update data to 2021' and female-only models with two fleets.

(ref:fig-bridge3-recruitment-french) French caption here

```{r bridge3-recruitment, fig.cap = ifelse(french, "(ref:fig-bridge3-recruitment-french)", "(ref:fig-bridge3-recruitment)"), out.width = "100%" , fig.pos="H"}
plot_ts_mpd(models$bridge_models[[3]],
            type = "rt",
            legend_title = "Bridge models - 2 fleets, 1 sex") +
  coord_cartesian(ylim = c(0, 0.4))
```

(ref:fig-bridge3-index-fits) Maximum Posterior Density (MPD) index fits for the 'Update data to 2021 data' and female-only models with two fleets.

(ref:fig-bridge3-index-fits-french) French caption here

```{r bridge3-index-fits, fig.cap = ifelse(french, "(ref:fig-bridge3-index-fits-french)", "(ref:fig-bridge3-index-fits)"), out.width = "100%" , fig.pos="H"}
plot_index_fit_mpd(
  models$bridge_models[[3]],
  surv_index = survey_index,
  point_size = 1,
  legend_title = "Bridge models - 2 fleets, 1 sex")
```

(ref:fig-bridge3-selectivities) Maximum Posterior Density (MPD) maturity ogives and selectivity estimates for all gears in the models with two fleets and one sex. The dashed blue and red lines are the male and female maturity ogives respectively, the blue and red lines with points are the yearly selectivity estimates for males and females respectively.

```{r bridge3-selectivities, fig.cap = "(ref:fig-bridge3-selectivities)"}
plist <- map2(models$bridge_models[[3]], names(models$bridge_models[[3]]), ~{
  plot_selex(.x, show_maturity = TRUE, title = .y) +
    theme(plot.title = element_text(face = "bold", size = 12),
          axis.text.x = element_text(size = 6),
          strip.text.x = element_text(size = 6))
})
n <- length(plist)
nrow <- floor(sqrt(n))
do.call("grid.arrange", c(plist, nrow = nrow))
```

\clearpage

```{r bridge3-param-settings-table, results = 'asis'}
param_settings_table(
  models$bridge_models[[3]][[2]],
  format = "latex",
  font_size = 7,
  caption = ifelse(
    french,
    "French goes here",
    "Number of parameters estimated, bounds, and prior parameterizations for the two-fleet model 'Change to two-fleet model'."))
```

```{r bridge3-param-table, results = 'asis'}
param_est_mpd_table(
  models$bridge_models[[3]],
  format = "latex",
  digits = 3,
  font_size = 7,
  model_col_widths = "5em",
  caption = ifelse(
    french,
    "French goes here",
    "Bridge model parameter estimates for the primary parameters, reference points, and catchability estimates ($q$) for each index for the models with two fleets and one sex.")) 
```

```{r bridge3-sel-param-table, results = 'asis'}
sel_param_est_mpd_table(
  models$bridge_models[[3]],
  format = "latex",
  digits = 3,
  font_size = 7,
  model_col_widths = "5em",
  caption = ifelse(
    french,
    "French goes here",
    "A comparison of Bridge model selectivity parameter estimates for the two-fleet, single-sex models."))  %>% 
  column_spec(1, width = "8em")
```

## Two-fleet split-sex models

Each model in this section is based on the previous one with only one change made so incremental changes can be tracked. The starting model here (*Add Discard CPUE*) is repeated from Section \@ref(single-fleet-female-only-models).

1. Convert model to split-sex.

1. Change fishing year to Feb. 21 - Feb 20.

1. Fixed male Natural mortality to be 0.2, and female to be 0.35. These are the values that are used in the Gulf of Alaska assessment.

<!-- 1. Fixed both male and female Natural mortality to be 0.2 to examine the effects on estimates of other parameters. -->

<!-- 1. Replace the 3 Synoptic surveys with the Stitched Synoptics index. This involved removing the Synoptic surveys as indices of abundance from the model but still using the age compositions from them. The Stitched Synoptics index was added as a second index of abundance with the Discard CPUE remaining as the first. -->

<!-- 1. Removed the QCS Synoptic survey as it was not fitting well. This model is based on the 'Change fishing year to Feb. 21 - Feb 20' model. -->

(ref:fig-bridge4-biomass) Maximum Posterior Density (MPD) estimates of spawning biomass (top panel) and relative spawning biomass (bottom panel) for the 'Add Discard CPUE' model and models with two fleets and two sexes.

(ref:fig-bridge4-biomass-french) French caption here

```{r bridge4-biomass, fig.cap = ifelse(french, "(ref:fig-bridge4-biomass-french)", "(ref:fig-bridge4-biomass)"), out.width = "100%" , fig.pos="H"}
cowplot::plot_grid(
  plot_ts_mpd(models$bridge_models[[4]],
              type = "sbt",
              legend_title = "Bridge models - 2 fleets, 2 sexes"),
  plot_ts_mpd(models$bridge_models[[4]],
              type = "sbt",
              rel = TRUE,
              legend_title = "Bridge models - 2 fleets, 2 sexes") + 
    coord_cartesian(ylim = c(0, 1)), nrow = 2)
```

(ref:fig-bridge4-recruitment) Maximum Posterior Density (MPD) estimates of recruitment for the 'Add Discard CPUE' model and models with two fleets and two sexes.

(ref:fig-bridge4-recruitment-french) French caption here

```{r bridge4-recruitment, fig.cap = ifelse(french, "(ref:fig-bridge4-recruitment-french)", "(ref:fig-bridge4-recruitment)"), out.width = "100%" , fig.pos="H"}
plot_ts_mpd(models$bridge_models[[4]],
            type = "rt",
            legend_title = "Bridge models - 2 fleets, 2 sexes") +
  coord_cartesian(ylim = c(0, 0.7))
```

(ref:fig-bridge4-index-fits) Maximum Posterior Density (MPD) index fits for the 'Add Discard CPUE' model and models with two fleets and two sexes.

(ref:fig-bridge4-index-fits-french) French caption here

```{r bridge4-index-fits, fig.cap = ifelse(french, "(ref:fig-bridge4-index-fits-french)", "(ref:fig-bridge4-index-fits)"), out.width = "100%" , fig.pos="H"}
plot_index_fit_mpd(models$bridge_models[[4]],
                   surv_index = survey_index,
                   legend_title = "Bridge models - 2 fleets, 2 sexes")
```

(ref:fig-bridge4-selectivities) Maximum Posterior Density (MPD) maturity ogives and selectivity estimates for all gears in the models with two fleets and two sexes. The dashed blue and red lines are the male and female maturity ogives respectively, the blue and red lines with points are the yearly selectivity estimates for males and females respectively.

```{r bridge4-selectivities, fig.cap = "(ref:fig-bridge4-selectivities)"}
plist <- map2(models$bridge_models[[4]], names(models$bridge_models[[4]]), ~{
  plot_selex(.x, show_maturity = TRUE, title = .y) +
    theme(plot.title = element_text(face = "bold", size = 12),
          axis.text.x = element_text(size = 6),
          strip.text.x = element_text(size = 6))
})
n <- length(plist)
nrow <- floor(sqrt(n))
do.call("grid.arrange", c(plist, nrow = nrow))
```

(ref:fig-bridge4-selectivity-possible-base) Closer view of the Maximum Posterior Density (MPD) maturity ogives and selectivity estimates for all gears in the 'Change fishing year to Feb 21 - Feb 20' model.

```{r selectivity-possible-base, fig.cap = "(ref:fig-bridge4-selectivity-possible-base)"}
plot_selex(models$bridge_models[[4]][[3]],
           show_maturity = TRUE,
           title = names(models$bridge_models[[4]])[3]) +
  theme(plot.title = element_text(face = "bold", size = 12),
        axis.text.x = element_text(size = 6),
        strip.text.x = element_text(size = 6))
```

(ref:fig-bridge4-age-fit-1) Maximum Posterior Density (MPD) age comp fits for the 'Change fishing year to Feb 21 - Feb 20' model, for the 'FT COMM' gear.

```{r bridge4-agefit-1, fig.cap = "(ref:fig-bridge4-age-fit-1)"}
plot_agecomp_fits_splitsex(models$bridge_models[[4]][[3]], 1)
```

(ref:fig-bridge4-age-fit-2) Maximum Posterior Density (MPD) age comp fits for the 'Change fishing year to Feb 21 - Feb 20' model, for the 'WB COMM' gear.

```{r bridge4-agefit-2, fig.cap = "(ref:fig-bridge4-age-fit-2)", fig.asp = 1.4}
plot_agecomp_fits_splitsex(models$bridge_models[[4]][[3]], 2)
```

(ref:fig-bridge4-age-fit-3) Maximum Posterior Density (MPD) age comp fits for the 'Change fishing year to Feb 21 - Feb 20' model, for the 'SYN QCS' gear.

```{r bridge4-agefit-3, fig.cap = "(ref:fig-bridge4-age-fit-3)"}
plot_agecomp_fits_splitsex(models$bridge_models[[4]][[3]], 3)
```

(ref:fig-bridge4-age-fit-5) Maximum Posterior Density (MPD) age comp fits for the 'Change fishing year to Feb 21 - Feb 20' model, for the 'SYN HS' gear.

```{r bridge4-agefit-5, fig.cap = "(ref:fig-bridge4-age-fit-5)"}
plot_agecomp_fits_splitsex(models$bridge_models[[4]][[3]], 5)
```
(ref:fig-bridge4-age-fit-6) Maximum Posterior Density (MPD) age comp fits for the 'Change fishing year to Feb 21 - Feb 20' model, for the 'SYN WCVI' gear.

```{r bridge4-agefit-6, fig.cap = "(ref:fig-bridge4-age-fit-6)"}
plot_agecomp_fits_splitsex(models$bridge_models[[4]][[3]], 6)
```

\clearpage

```{r bridge4-param-settings-table, results = 'asis'}
param_settings_table(
  models$bridge_models[[4]][[2]],
  format = "latex",
  font_size = 7,
  caption = ifelse(
    french,
    "French goes here",
    "Number of parameters estimated, bounds, and prior parameterizations for the two-fleet model 'Convert model to split sex'."))
```

```{r bridge4-param-table, results = 'asis'}
param_est_mpd_table(
  models$bridge_models[[4]],
  format = "latex",
  digits = 3,
  font_size = 7,
  model_col_widths = "5em",
  caption = ifelse(
    french,
    "French goes here",
    "Bridge model parameter estimates for the primary parameters, reference points, and catchability estimates ($q$) for each index for the models with two fleets and two sexes.")) 
```

```{r bridge4-sel-param-table, results = 'asis'}
sel_param_est_mpd_table(
  models$bridge_models[[4]],
  format = "latex",
  digits = 3,
  font_size = 7,
  model_col_widths = "5em",
  caption = ifelse(
    french,
    "French goes here",
    "A comparison of Bridge model selectivity parameter estimates for the two-fleet, two-sex models.")) %>% 
  column_spec(1, width = "8em")
```


