## BRIDGE MODEL FIGURES

(ref:fig-bridge-group1-biomass-en) MCMC estimates of spawning biomass (left panel) and relative spawning biomass (right panel) for the first four bridging models. Points and bars on the left in the left panel represent $B_0$ values and 95% credible interval. The first model in the legend has a shaded ribbon representing the credible interval (CI), the others have dotted lines the same colour as the medians which represent the CI.

(ref:fig-bridge-group1-biomass-fr) French caption here

```{r bridge-biomass-group1, fig.cap = ifelse(fr(), "(ref:fig-bridge-group1-biomass-fr)", "(ref:fig-bridge-group1-biomass-en)"), out.width = "100%"}
cowplot::plot_grid(
  plot_biomass_mcmc(models$bridge_grps[[1]],
                    legend_title = "Bridge models group 1",
                    angle_x_labels = TRUE,
                    ylim = c(0, 1000)) +
    theme(legend.key.size = unit(0.1, 'cm')),
  plot_biomass_mcmc(models$bridge_grps[[1]],
                    rel = TRUE,
                    leg_loc = NULL,
                    angle_x_labels = TRUE,
                    ylim = c(0, 1.5)),
  ncol = 2)

```

(ref:fig-bridge-group2-biomass-en) MCMC estimates of spawning biomass (left panel) and relative spawning biomass (right panel) for the second group of bridging models. See Figure \@ref(fig:bridge-biomass-group1) for more information.

(ref:fig-bridge-group2-biomass-fr) French caption here

```{r bridge-biomass-group2, fig.cap = ifelse(fr(), "(ref:fig-bridge-group2-biomass-fr)", "(ref:fig-bridge-group2-biomass-en)"), out.width = "100%"}
cowplot::plot_grid(
  plot_biomass_mcmc(models$bridge_grps[[2]],
                    legend_title = "Bridge models group 2",
                    angle_x_labels = TRUE,
                    ylim = c(0, 300)) +
    theme(legend.key.size = unit(0.1, 'cm')),
  plot_biomass_mcmc(models$bridge_grps[[2]],
                    rel = TRUE,
                    leg_loc = NULL,
                    angle_x_labels = TRUE,
                    ylim = c(0, 1.5)),
  ncol = 2)

```

(ref:fig-bridge-group1-index-en) MCMC fits to the indices of abundance for the first group of bridging models.

(ref:fig-bridge-group1-index-fr) French caption here

```{r bridge-index-group1, fig.cap = ifelse(fr(), "(ref:fig-bridge-group1-index-fr)", "(ref:fig-bridge-group1-index-en)"), out.width = "100%"}
plot_index_mcmc(models$bridge_grps[[1]],
                type = "fits",
                surv_index = survey_index,
                leg_loc = "facet",
                text_title_size = NULL,
                base_color = "royalblue")
```

(ref:fig-bridge-group2-index-en) MCMC fits to the indices of abundance for the second group of bridging models.

(ref:fig-bridge-group2-index-fr) French caption here

```{r bridge-index-group2, fig.cap = ifelse(fr(), "(ref:fig-bridge-group2-index-fr)", "(ref:fig-bridge-group2-index-en)"), out.width = "100%"}
plot_index_mcmc(models$bridge_grps[[2]],
                type = "fits",
                surv_index = survey_index,
                leg_loc = c(0.55, 1),
                leg_size = 0.3,
                leg_text_size = 3,
                text_title_size = NULL,
                base_color = "royalblue")
```

(ref:fig-bridge-group3-biomass-en) MCMC estimates of spawning biomass (left panel) and relative spawning biomass (right panel) for the third group of bridging models. See Figure \@ref(fig:bridge-biomass-group1) for more information.

(ref:fig-bridge-group3-biomass-fr) French caption here

```{r bridge-biomass-group3, fig.cap = ifelse(fr(), "(ref:fig-bridge-group3-biomass-fr)", "(ref:fig-bridge-group3-biomass-en)"), out.width = "100%"}
cowplot::plot_grid(
  plot_biomass_mcmc(models$bridge_grps[[3]],
                    legend_title = "Bridge models group 3",
                    angle_x_labels = TRUE,
                    ylim = c(0, 300)) +
    theme(legend.key.size = unit(0.1, 'cm')),
  plot_biomass_mcmc(models$bridge_grps[[3]],
                    rel = TRUE,
                    leg_loc = NULL,
                    angle_x_labels = TRUE,
                    ylim = c(0, 1.5)),
  ncol = 2)

```

<!-- (ref:fig-bridge-index-resids) Log standardized residuals for the indices used in the first four bridge models. -->

<!-- ```{r bridge-index-resids-qcs, fig.cap = "(ref:fig-bridge-index-resid-qcs)", fig.pos = "H"} -->
<!-- legend <- cowplot::get_legend(plot_index_mcmc(models$bridge_grps[[1]], -->
<!--                                               type = "resids", -->
<!--                                               gear = 1, -->
<!--                                               surv_index = survey_index)) -->
<!-- p <- cowplot::plot_grid( -->
<!--   plot_index_mcmc(models$bridge_grps[[1]], -->
<!--                   type = "resids", -->
<!--                   gear = 1, -->
<!--                   surv_index = survey_index, -->
<!--                   leg_loc = NULL), -->
<!--   plot_index_mcmc(models$bridge_grps[[1]], -->
<!--                   type = "resids", -->
<!--                   gear = 2, -->
<!--                   surv_index = survey_index, -->
<!--                   leg_loc = NULL), -->
<!--   plot_index_mcmc(models$bridge_grps[[1]], -->
<!--                   type = "resids", -->
<!--                   gear = 3, -->
<!--                   surv_index = survey_index, -->
<!--                   leg_loc = NULL), -->
<!--   plot_index_mcmc(models$bridge_grps[[1]], -->
<!--                   type = "resids", -->
<!--                   gear = 4, -->
<!--                   surv_index = survey_index, -->
<!--                   leg_loc = NULL), -->
<!--   plot_index_mcmc(models$bridge_grps[[1]], -->
<!--                   type = "resids", -->
<!--                   gear = 5, -->
<!--                   surv_index = survey_index, -->
<!--                   leg_loc = NULL)) -->
<!--   # Place legend in empty grid cell -->
<!--   p + cowplot::draw_grob(legend, 2/3, -1/6, 1/3, 0.5) -->
<!-- ``` -->

\clearpage
