## MCMC DIAGNOSTIC FIGURES FOR THE BASE MODEL

(ref:fig-base-priors-posts-en) Prior probability distributions used in the base model (blue shaded areas) overlaid with posterior distribution histograms. The solid red line is the mode of the prior distribution, the vertical solid black line is the mean of the prior, and the vertical dashed black lines represent one standard deviation from the mean. Plots that are entirely shaded blue show uniform priors which are shaded underneath the prior value.

(ref:fig-base-priors-posts-fr)  Distributions de probabilité antérieures utilisées dans le modèle de base (zones ombrées en bleu) superposées aux histogrammes de distribution postérieure. La ligne rouge pleine est le mode de la distribution antérieure, la ligne noire pleine verticale est la moyenne de la distribution antérieure, et les lignes noires pointillées verticales représentent un écart type de la moyenne. Les graphiques qui sont entièrement ombrés en bleu montrent des antériorités uniformes qui sont ombrées sous la valeur de l'antériorité.

```{r fig-base-priors-posts, fig.cap = ifelse(fr(), "(ref:fig-base-priors-posts-fr)", "(ref:fig-base-priors-posts-en)")}
plot_priors_posts_mcmc(base_model,
                       param_rm = c("sel",
                                    "bo",
                                    "tau",
                                    "sigma",
                                    "log_m_sex1",
                                    "log_m_sex2"),
                       text_title_size = NULL)
```

(ref:fig-base-trace-en) Trace plots for MCMC output of estimated lead parameters in the base model. The MCMC run has chain length `r f(mcmc_chain_length)` with a sample taken every `r f(mcmc_sample_freq)`^th^ iteration. Of the `r f(mcmc_num_samples)` samples taken, the first `r f(mcmc_burn_in)` were removed as a burn-in period. MSY-base parameters have numerical subscripts of either 1 or 2; those correspond to the two commercial trawl fleets, `r base_model$dat$fleet_gear_names[1]` and `r base_model$dat$fleet_gear_names[2]` respectively. $q$ parameters represent catchability for the survey indices, with numerical indices representing: `r paste(base_index_gears$gear, " = ", base_index_gears$gear_name, collapse = ", ")`.

(ref:fig-base-trace-fr) Tracés pour la sortie MCMC des paramètres de plomb estimés dans le modèle de base. L'exécution MCMC a une longueur de chaîne `r f(mcmc_chain_length)` avec un échantillon pris chaque `r f(mcmc_sample_freq)`^ème^ itération. Parmi les `r f(mcmc_num_samples)` échantillons prélevés, les premiers `r f(mcmc_burn_in)` ont été retirés comme période de burn-in. Les paramètres de base du RMD ont des indices numériques de 1 ou 2 ; ils correspondent aux deux flottes de chalutage commercial, respectivement `r base_model$dat$fleet_gear_names[1]` et `r base_model$dat$fleet_gear_names[2]`. Les paramètres $q$ représentent la capturabilité pour les indices de l'enquête, les indices numériques représentant : `r paste(base_index_gears$gear, " = ", base_index_gears$gear_name, collapse = ", ")`.

```{r fig-base-trace, fig.cap = ifelse(fr(), "(ref:fig-base-trace-fr)", "(ref:fig-base-trace-en)")}
plot_traces_mcmc(base_model,
                 plot_sel = FALSE, 
                 param_rm = c("m1", "m2", "rho", "ssb"),
                 text_title_size = NULL)
```

(ref:fig-base-autocor-en) Autocorrelation plots for MCMC output of estimated lead parameters in the base model. The x-axis values are the lag between posteriors. See Figure \@ref(fig:fig-base-trace) for parameter descriptions.

(ref:fig-base-autocor-fr) Graphiques d'autocorrélation pour la sortie MCMC des paramètres de plomb estimés dans le modèle de base. Les valeurs de l'axe des x sont le décalage entre les postérieurs.

```{r fig-base-autocor, fig.cap = ifelse(fr(), "(ref:fig-base-autocor-fr)", "(ref:fig-base-autocor-en)")}
plot_autocorr_mcmc(base_model,
                   plot_sel = FALSE, 
                   param_rm = c("m1", "m2", "rho", "ssb"),
                   text_title_size = NULL,
                   lag_max = 1000,
                   col = "blue",
                   lwd = 2)
```

(ref:fig-base-trace-selex-en) Trace plots for MCMC output of estimated selectivity parameters in the base model. $\hat{a}$ are the estimates of selectivity-at-age-50%, $\hat{\gamma}$ are the estimated standard deviations on selectivity-at-age-50%. The letter subscripts F and M correspond to female and male, and the numerical subscripts represent the gear as follows: `r paste(base_all_gears$gear, " = ", base_all_gears$gear_name, collapse = ", ")`.

(ref:fig-base-trace-selex-fr) French here

```{r fig-base-trace-selex, fig.cap = ifelse(fr(), "(ref:fig-base-trace-selex-fr)", "(ref:fig-base-trace-selex-en)")}
plot_traces_mcmc(base_model,
                 plot_sel = TRUE, 
                 text_title_size = NULL)
```

(ref:fig-base-autocor-selex-en) Autocorrelation plots for MCMC output of estimated selectivity parameters in the base model.  The x-axis values are the lag between posteriors. See Figure \@ref(fig:fig-base-trace-selex) for parameter descriptions.

(ref:fig-base-autocor-selex-fr) Graphiques d'autocorrélation pour la sortie MCMC des paramètres de sélectivité estimés dans le modèle de base.  Les valeurs de l'axe des x sont le décalage entre les postérieurs. Voir la figure \@ref(fig:fig-base-trace-selex) pour la description des paramètres.

```{r fig-base-autocor-selex, fig.cap = ifelse(fr(), "(ref:fig-base-autocor-selex-fr)", "(ref:fig-base-autocor-selex-en)")}
plot_autocorr_mcmc(base_model, 
                   plot_sel = TRUE, 
                   text_title_size = NULL,
                   lag_max = 1000,
                   col = "blue",
                   lwd = 2)
```

(ref:fig-base-pairs-en) Pairs plots for MCMC estimated parameters in the base model. The lines in the points plots in the lower triangular panels are linear models with shaded 95% confidence intervals. The line plots in the diagonal panels represent density of the parameter values, and the values in the upper triangular panels are the correlations between parameters with text size being directly proportional to the absolute value of those values. See Figure \@ref(fig:fig-base-trace) for parameter descriptions.

(ref:fig-base-pairs-fr) Diagrammes de paires pour les paramètres estimés par MCMC dans le modèle de base. Les lignes dans les tracés de points dans les panneaux triangulaires inférieurs sont des modèles linéaires avec des intervalles de confiance à 95% ombrés. Les tracés de lignes dans les panneaux diagonaux représentent la densité des valeurs des paramètres, et les valeurs dans les panneaux triangulaires supérieurs sont les corrélations entre les paramètres, la taille du texte étant directement proportionnelle à la valeur absolue de ces valeurs. Voir la figure \@ref(fig:fig-base-trace) pour la description des paramètres.

```{r fig-base-pairs, fig.cap = ifelse(fr(), "(ref:fig-base-pairs-fr)", "(ref:fig-base-pairs-en)")}
plot_pairs_mcmc(base_model,
                plot_sel = FALSE,
                param_rm = c("m1", "m2", "rho", "ssb",
                             "msy1", "msy2",
                             "fmsy1", "fmsy2",
                             "umsy1", "umsy2",
                             "bmsy", "bo", "sbo"),
                text_title_size = NULL,
                tick_label_size = 4,
                point_size = 0.5)
```

(ref:fig-base-pairs-sel-en) Pairs plots for MCMC estimated selectivity parameters in the base model. The lines in the points plots in the lower triangular panels are linear models with shaded 95% confidence intervals. The line plots in the diagonal panels represent density of the parameter values, and the values in the upper triangular panels are the correlations between parameters with text size being directly proportional to the absolute value of those values. See Figure \@ref(fig:fig-base-trace-selex) for parameter descriptions.

(ref:fig-base-pairs-sel-fr) French here

```{r fig-base-pairs-sel, fig.cap = ifelse(fr(), "(ref:fig-base-pairs-sel-fr)", "(ref:fig-base-pairs-sel-en)")}
# Remove 4 and 7 because they are fixed in the model (HSMAS and DCPUE indices) and will produce NAs
plot_pairs_mcmc(base_model,
                plot_sel = TRUE,
                param_rm = c("selage4_male_block1",
                             "selage4_female_block1",
                             "selsd4_male_block1",
                             "selsd4_female_block1",
                             "selage7_male_block1",
                             "selage7_female_block1",
                             "selsd7_male_block1",
                             "selsd7_female_block1"),
                text_title_size = NULL,
                tick_label_size = 4,
                point_size = 0.25)
```

\clearpage
