## Sensitivity model figures

<!-- Vartheta and sigma, and steepness  -------------------------------------->

(ref:fig-sens-variance-en) Spawning biomass for sensitivities to changes in the $\vartheta^2$ and $\rho$ (by way of a change in $\sigma$), $\tau$, and steepness ($h$) parameters.

(ref:fig-sens-variance-fr) French here

```{r fig-sens-variance, fig.cap = ifelse(fr(), "(ref:fig-sens-variance-fr)", "(ref:fig-sens-variance-en)")}
plot_biomass_mcmc(models$sens_grps[[1]],
                  angle_x_labels = TRUE,
                  text_title_size = NULL,
                  show_bo_lines = TRUE,
                  ylim = c(0, 300))
```

(ref:fig-sens-variance-rel-en) Relative spawning biomass for sensitivities to changes in the $\vartheta^2$ (by way of a change in $\sigma$), $\tau$, and steepness ($h$) parameters.

(ref:fig-sens-variance-rel-fr) French here

```{r fig-sens-variance-rel, fig.cap = ifelse(fr(), "(ref:fig-sens-variance-rel-fr)", "(ref:fig-sens-variance-rel-en)")}
plot_biomass_mcmc(models$sens_grps[[1]],
                  rel = TRUE,
                  angle_x_labels = TRUE,
                  text_title_size = NULL,
                  show_bo_lines = TRUE,
                  ylim = c(0, 2))
```

(ref:fig-sens-variance-prior-post-en) Relative spawning biomass for sensitivities to changes in the $\vartheta^2$ (by way of a change in $\sigma$), $\tau$, and steepness ($h$) parameters.

(ref:fig-sens-variance-prior-post-fr) French here

```{r fig-sens-variance-prior-post, fig.cap = ifelse(fr(), "(ref:fig-sens-variance-prior-post-fr)", "(ref:fig-sens-variance-prior-post-en)")}
plot_priors_posts_mcmc(models$sens_grps[[1]][[2]],
                       param_rm = c("sel",
                                    "bo",
                                    "tau",
                                    "sigma",
                                    "log_m_sex1",
                                    "log_m_sex2"))
```

(ref:fig-sens-group1-index-en) MCMC fits to the indices of abundance for the first group of sensitivity models.

(ref:fig-sens-group1-biomass-fr) French caption here

```{r sens-index-group1, fig.cap = ifelse(fr(), "(ref:fig-sens-group1-index-fr)", "(ref:fig-sens-group1-index-en)"), out.width = "100%"}
plot_index_mcmc(models$sens_grps[[1]],
                type = "fits",
                surv_index = survey_index,
                leg_loc = "facet",
                text_title_size = NULL,
                base_color = "royalblue")
```


(ref:fig-sens-steepness-prior-en) Priors and posteriors for the sensitivity to steepness prior change. This should be compared with the base model in Figure \@ref(fig:fig-base-priors-posts).

(ref:fig-sens-steepness-prior-fr) French caption here

```{r sens-steepness-prior, fig.cap = ifelse(fr(), "(ref:fig-sens-steepness-prior-fr)", "(ref:fig-sens-steepness-prior-en)"), out.width = "100%"}
plot_priors_posts_mcmc(models$sens_grps[[1]][[5]],
                       param_rm = c("sel",
                                    "bo",
                                    "tau",
                                    "sigma",
                                    "log_m_sex1",
                                    "log_m_sex2"),
                       text_title_size = NULL)
```

<!-- Natural mortality ------------------------------------------------------->

(ref:fig-sens-m-en) Spawning biomass for sensitivities including changes in the natural mortality ($M$) parameters. In the base model, this parameter is fixed for both male and females. In these sensitivities, it is estimated in addition to the changes in prior.

(ref:fig-sens-m-fr) French here

```{r fig-sens-m, fig.cap = ifelse(fr(), "(ref:fig-sens-m-fr)", "(ref:fig-sens-m-en)")}
plot_biomass_mcmc(models$sens_grps[[2]],
                  angle_x_labels = TRUE,
                  text_title_size = NULL,
                  show_bo_lines = TRUE)
```

(ref:fig-sens-m-rel-en) Relative spawning biomass for sensitivities pertaining to changes in the natural mortality ($M$) parameters.

(ref:fig-sens-m-rel-fr) French here

```{r fig-sens-m-rel, fig.cap = ifelse(fr(), "(ref:fig-sens-m-rel-fr)", "(ref:fig-sens-m-rel-en)")}
plot_biomass_mcmc(models$sens_grps[[2]],
                  rel = TRUE,
                  angle_x_labels = TRUE,
                  text_title_size = NULL,
                  show_bo_lines = TRUE)
```

<!-- Catchability ------------------------------------------------------------>

(ref:fig-sens-q-en) Spawning biomass for the sensitivities to changes in the Catchability ($q_k$) parameters. For these sensitivities all gears ($k$) are modified in the same way.

(ref:fig-sens-q-fr) French here

```{r fig-sens-q-m, fig.cap = ifelse(fr(), "(ref:fig-sens-q-fr)", "(ref:fig-sens-q-en)")}
plot_biomass_mcmc(models$sens_grps[[3]],
                  angle_x_labels = TRUE,
                  text_title_size = NULL,
                  show_bo_lines = TRUE)
```

(ref:fig-sens-q-rel-en) Relative spawning biomass for the sensitivities to changes in the Catchability ($q_k$) parameters.

(ref:fig-sens-q-rel-fr) French here

```{r fig-sens-q-rel, fig.cap = ifelse(fr(), "(ref:fig-sens-q-rel-fr)", "(ref:fig-sens-q-rel-en)")}
plot_biomass_mcmc(models$sens_grps[[3]],
                  rel = TRUE,
                  angle_x_labels = TRUE,
                  text_title_size = NULL,
                  show_bo_lines = TRUE)
```

<!-- Selectivity and Geostat surveys ----------------------------------------->

(ref:fig-sens-selex-en) Spawning biomass for the sensitivities to changes in the Selectivity ($\hat{a}_k$ and $\gamma_k$) parameters and to a change from design-basded survey indices to geostatistical-based survey indices. Fot the selectivity sensitivity, the selectivities for the two commercial trawl fisheries are set equal to the maturity for the two commercial trawl gears ($k$).

(ref:fig-sens-selex-fr) French here

```{r fig-sens-selex-m, fig.cap = ifelse(fr(), "(ref:fig-sens-selex-fr)", "(ref:fig-sens-selex-en)")}
plot_biomass_mcmc(models$sens_grps[[4]],
                  angle_x_labels = TRUE,
                  text_title_size = NULL,
                  show_bo_lines = TRUE)
```

(ref:fig-sens-selex-rel-en) Relative spawning biomass for the sensitivities to changes in the Selectivity ($\hat{a}_k$ and $\gamma_k$) parameters, and to a change from design-basded survey indices to geostatistical-based survey indices.

(ref:fig-sens-selex-rel-fr) French here

```{r fig-sens-selex-rel, fig.cap = ifelse(fr(), "(ref:fig-sens-selex-rel-fr)", "(ref:fig-sens-selex-rel-en)")}
plot_biomass_mcmc(models$sens_grps[[4]],
                  rel = TRUE,
                  angle_x_labels = TRUE,
                  text_title_size = NULL,
                  show_bo_lines = TRUE)
```


\clearpage
