## Retrospective figures for the base model

(ref:fig-retro-biomass-en) Spawning biomass retrospectives.

(ref:fig-retro-biomass-fr) French here

```{r fig-retro-biomass, fig.cap = ifelse(fr(), "(ref:fig-retro-biomass-fr)", "(ref:fig-retro-biomass-en)")}
plot_biomass_mcmc(models$retro_grps[[1]],
                  angle_x_labels = TRUE,
                  text_title_size = NULL,
                  show_bo_lines = TRUE,
                  bo_refpt_colors = c("salmon", "darkgreen"),
                  ylim = c(0, 250))

```

(ref:fig-retro-biomass-rel-en) Relative spawning biomass retrospectives.

(ref:fig-retro-biomass-rel-fr) French here

```{r fig-retro-biomass-rel, fig.cap = ifelse(fr(), "(ref:fig-retro-biomass-rel-fr)", "(ref:fig-retro-biomass-rel-en)")}
plot_biomass_mcmc(models$retro_grps[[1]],
                  angle_x_labels = TRUE,
                  text_title_size = NULL,
                  show_bo_lines = TRUE,
                  rel = TRUE,
                  bo_refpt_colors = c("salmon", "darkgreen"),
                  ylim = c(0, 2))

```

(ref:fig-retro-recr-en) Recruitment of `r sp` for the retrospective models.
The points are the medians of the posteriors, the vertical lines
are the 95% Credible intervals for the posteriors, the points at $R_0$
are the median estimates for the initial recruitment parameters $R_0$,
and the vertical lines over those points is the 95% Credible interval
for $R_0$. The shaded ribbon is the $R_0$ credible interval across the
whole time series for the base model. The models are slightly offset from
each other for ease of viewing.

(ref:fig-retro-recr-fr) French here

```{r fig-retro-recr, fig.cap = ifelse(fr(), "(ref:fig-retro-recr-fr)", "(ref:fig-retro-recr-en)")}
plot_recr_mcmc(models$retro_grps[[1]],
               angle_x_labels = TRUE,
               text_title_size = NULL,
               leg_loc = c(0,1))
```

(ref:fig-retro-f-en) Fishing mortality for the base and retrospective models
for the two trawl fisheries. The shaded area represents the 95% credible
interval for the base model, the dotted lines represent the 95% credible
interval for the retrospective models.

(ref:fig-base-f-fr) French here

```{r fig-retro-f, fig.cap = ifelse(fr(), "(ref:fig-retro-f-fr)", "(ref:fig-retro-f-en)")}
plot_f_mcmc(models$retro_grps[[1]],
            angle_x_labels = TRUE,
            text_title_size = NULL,
            leg_loc = c(0, 1))
```

(ref:fig-retro-index-fits-en) Index fits for the base and retrospective models. The light grey points and vertical lines show the index values and CVs; the other colored points show the medians of the posteriors; the solid vertical lines show the 95% credible intervals for the posteriors. The lines connecting points along the time series are only present for aesthetic value.

(ref:fig-retro-index-fits-fr) French here

```{r fig-retro-index-fits, fig.cap = ifelse(fr(), "(ref:fig-retro-index-fits-fr)", "(ref:fig-retro-index-fits-en)")}
plot_index_mcmc(models$retro_grps[[1]],
                type = "fits",
                surv_index = survey_index,
                leg_loc = "facet",
                text_title_size = NULL,
                base_color = "royalblue",
                errbar_width = 0.1,
                dodge = 0.1)
```

(ref:fig-retro-index-resids-en) Index Log standardized residuals for the base and retrospective models. The vertical lines represent the 95% credible intervals.

(ref:fig-retro-index-resids-fr) French here

```{r fig-retro-index-resids, fig.cap = ifelse(fr(), "(ref:fig-retro-index-resids-fr)", "(ref:fig-retro-index-resids-en)")}
plot_index_mcmc(models$retro_grps[[1]],
                type = "resids",
                surv_index = survey_index,
                leg_loc = "facet",
                text_title_size = NULL,
                base_color = "royalblue",
                errbar_width = 0.1,
                dodge = 0.1)
```
