## PROJECTION FIGURES FOR THE BASE MODEL

(ref:fig-rel-biomass-proj-en) Relative spawning biomass of `r sp` for the base model with $B_0$-based reference points and projections into the future. The constant catch values are shown as text on the right of the end points of each projected trajectory. See the decision table (Table \@ref(tab:decision-table)) for probabilities of being under reference points and of the stock declining for each catch stream.

(ref:fig-rel-biomass-proj-fr) French here

```{r fig-rel-biomass-proj, fig.cap = ifelse(fr(), "(ref:fig-rel-biomass-proj-fr)", "(ref:fig-rel-biomass-proj-en)")}
plot_biomass_proj_mcmc(base_model,
                       palette = "Spectral",
                       leg_loc = NULL,
                       rel = TRUE,
                       xlim = c(1997, 2026),
                       ylim = c(0, 1.2),
                       show_bo_lines = TRUE,
                       angle_x_labels = TRUE,
                       line_width = 0.5,
                       point_size = 1,
                       label_font_size = 3)
```

(ref:fig-rel-biomass-proj-closeup-en) Closeup view of relative spawning biomass for the `r sp` base model with $B_0$-based reference points and projections into the future. The constant catch values are shown as text on the right of the end points of each projected trajectory. See the decision table (Table \@ref(tab:decision-table)) for probabilities of being under reference points and of the stock declining for each catch stream.

(ref:fig-rel-biomass-proj-closeup-fr) French here

```{r fig-rel-biomass-proj-closeup, fig.cap = ifelse(fr(), "(ref:fig-rel-biomass-proj-closeup-fr)", "(ref:fig-rel-biomass-proj-closeup-en)")}
plot_biomass_proj_mcmc(base_model,
                       palette = "Spectral",
                       leg_loc = NULL,
                       rel = TRUE,
                       xlim = c(2020, 2026),
                       ylim = c(0, 0.9),
                       show_bo_lines = TRUE,
                       angle_x_labels = TRUE,
                       line_width = 0.5,
                       point_size = 1,
                       label_font_size = 3)
```

(ref:fig-catch-streams-proj-nextyr-en) Projected `r base_model$dat$end.yr + 2` relative spawning biomass for catch occurring in `r base_model$dat$end.yr + 1`. Black points are medians of the posterior, thick lines are the 50% CI (25%--75%), and thin lines are the 95% CI (2.5%--97.5%). The solid red line is the LRP, $0.2B_0$, the dotted blue line is the $0.35B_0$ line, and the dashed green line is the USR, $0.4B_0$.

(ref:fig-catch-streams-proj-nextyr-fr) French here

```{r fig-catch-streams-nextyr-proj, fig.cap = ifelse(fr(), "(ref:fig-catch-streams-proj-nextyr-fr)", "(ref:fig-catch-streams-proj-nextyr-en)")}
plot_dfo_ref_point_figure(base_model, biomass_col = "B2023")
```

(ref:fig-catch-streams-proj-nextnextyr-en) Projected `r base_model$dat$end.yr + 3` relative spawning biomass for catch occurring in `r base_model$dat$end.yr + 2`. Black points are medians of the posterior, thick lines are the 50% CI (25%--75%), and thin lines are the 95% CI (2.5%--97.5%). The solid red line is the LRP, $0.2B_0$, the dotted blue line is the $0.35B_0$ line, and the dashed green line is the USR, $0.4B_0$.

(ref:fig-catch-streams-proj-nextnextyr-fr) French here

```{r fig-catch-streams-nextnextyr-proj, fig.cap = ifelse(fr(), "(ref:fig-catch-streams-proj-nextnextyr-fr)", "(ref:fig-catch-streams-proj-nextnextyr-en)")}
plot_dfo_ref_point_figure(base_model, biomass_col = "B2024")
```

(ref:fig-catch-streams-proj-nextnextnextyr-en) Projected `r base_model$dat$end.yr + 4` relative spawning biomass for catch occurring in `r base_model$dat$end.yr + 3`. Black points are medians of the posterior, thick lines are the 50% CI (25%--75%), and thin lines are the 95% CI (2.5%--97.5%). The solid red line is the LRP, $0.2B_0$, the dotted blue line is the $0.35B_0$ line, and the dashed green line is the USR, $0.4B_0$.

(ref:fig-catch-streams-proj-nextnextnextyr-fr) French here

```{r fig-catch-streams-nextnextnextyr-proj, fig.cap = ifelse(fr(), "(ref:fig-catch-streams-proj-nextnextnextyr-fr)", "(ref:fig-catch-streams-proj-nextnextnextyr-en)")}
plot_dfo_ref_point_figure(base_model, biomass_col = "B2025")
```

(ref:fig-catch-streams-proj-nextnextnextnextyr-en) Projected `r base_model$dat$end.yr + 5` relative spawning biomass for catch occurring in `r base_model$dat$end.yr + 4`. Black points are medians of the posterior, thick lines are the 50% CI (25%--75%), and thin lines are the 95% CI (2.5%--97.5%). The solid red line is the LRP, $0.2B_0$, the dotted blue line is the $0.35B_0$ line, and the dashed green line is the USR, $0.4B_0$.

(ref:fig-catch-streams-proj-nextnextnextnextyr-fr) French here

```{r fig-catch-streams-nextnextnextnextyr-proj, fig.cap = ifelse(fr(), "(ref:fig-catch-streams-proj-nextnextnextnextyr-fr)", "(ref:fig-catch-streams-proj-nextnextnextnextyr-en)")}
plot_dfo_ref_point_figure(base_model, biomass_col = "B2026")
```
