## PROJECTION FIGURES FOR THE BASE MODEL

(ref:fig-rel-biomass-proj-en) Estimated relative spawning biomass ($B_t/B_0$) for the base model. The shaded area represents the 95% credible interval (CI) and the solid line with points represents the median. Horizontal lines indicate the $0.2B_0$ (solid red) and $0.4B_0$ (dashed green) reference points. The colored dots from 2023 to 2026 are the medians of the posteriors for the projected catch levels, with solid lines connecting them; the dashed lines from 2023 to 2026 represent the 95% CIs for those posteriors. The constant catch values are shown as text on the right of the end points of each projected trajectory. See the decision table (Table \@ref(tab:decision-table)) for probabilities of being under reference points and of the stock declining for each catch level.

(ref:fig-rel-biomass-proj-fr)  Estimation de la biomasse féconde relative ($B_t/B_0$) pour le modèle de base. La zone ombrée représente l'intervalle de crédibilité (IC) à 95% et la ligne continue avec des points représente la médiane. Les lignes horizontales indiquent les points de référence $0,2B_0$ (rouge plein) et $0,4B_0$ (vert pointillé). Les points colorés de 2023 à 2026 sont les médianes des valeurs postérieures pour les niveaux de capture projetés, avec des lignes solides les reliant ; les lignes en pointillé de 2023 à 2026 représentent les IC à 95 % pour ces valeurs postérieures. Les valeurs de captures constantes sont indiquées sous forme de texte à droite des points d'arrivée de chaque trajectoire projetée. Voir la table de décision (Tableau \@ref(tab:decision-table)) pour les probabilités d'être en dessous des points de référence et de voir le stock décliner pour chaque niveau de capture.

```{r fig-rel-biomass-proj, fig.cap = ifelse(fr(), "(ref:fig-rel-biomass-proj-fr)", "(ref:fig-rel-biomass-proj-en)")}
plot_biomass_proj_mcmc(base_model,
                       palette = "Spectral",
                       leg_loc = NULL,
                       rel = TRUE,
                       xlim = c(1997, 2026),
                       ylim = c(0, 1.2),
                       show_bo_lines = TRUE,
                       angle_x_labels = TRUE,
                       line_width = 0.5,
                       point_size = 1,
                       label_font_size = 3)
```

(ref:fig-rel-biomass-proj-closeup-en) Closeup view of relative spawning biomass for the `r sp` base model with $B_0$-based reference points and projections into the future. The constant catch values are shown as text on the right of the end points of each projected trajectory. See the decision table (Table \@ref(tab:decision-table)) for probabilities of being under reference points and of the stock declining for each catch stream.

(ref:fig-rel-biomass-proj-closeup-fr) Vue rapprochée de la biomasse reproductrice relative pour le modèle de base `r sp` avec des points de référence basés sur $B_0$ et des projections dans l'avenir. Les valeurs des captures constantes sont indiquées sous forme de texte à droite des points finaux de chaque trajectoire projetée. Voir la table de décision (Tableau \@ref(tab:decision-table)) pour les probabilités d'être en dessous des points de référence et de voir le stock décliner pour chaque flux de capture.

```{r fig-rel-biomass-proj-closeup, fig.cap = ifelse(fr(), "(ref:fig-rel-biomass-proj-closeup-fr)", "(ref:fig-rel-biomass-proj-closeup-en)")}
plot_biomass_proj_mcmc(base_model,
                       palette = "Spectral",
                       leg_loc = NULL,
                       rel = TRUE,
                       xlim = c(2020, 2026),
                       ylim = c(0, 0.9),
                       show_bo_lines = TRUE,
                       angle_x_labels = TRUE,
                       line_width = 0.5,
                       point_size = 1,
                       label_font_size = 3,
                       nudge_catch_labels = c(-0.1, 0))
```

(ref:fig-catch-streams-proj-nextyr-en) Projected `r base_model$dat$end.yr + 2` relative spawning biomass for catch occurring in `r base_model$dat$end.yr + 1`. Black points are medians of the posterior, thick lines are the 50% CI (25%--75%), and thin lines are the 95% CI (2.5%--97.5%). The solid red line is the LRP, $0.2B_0$, the dotted blue line is the $0.35B_0$ line, and the dashed green line is the USR, $0.4B_0$.

(ref:fig-catch-streams-proj-nextyr-fr) Biomasse reproductrice relative projetée `r base_model$dat$end.yr + 2` pour les captures effectuées en `r base_model$dat$end.yr + 1`. Les points noirs sont les médianes du postérieur, les lignes épaisses sont l'IC à 50 % (25 %--75 %) et les lignes fines sont l'IC à 95 % (2,5 %--97,5 %). La ligne rouge continue est la LRP, $0,2B_0$, la ligne bleue pointillée est la ligne $0,35B_0$, et la ligne verte pointillée est l'USR, $0,4B_0$.

```{r fig-catch-streams-nextyr-proj, fig.cap = ifelse(fr(), "(ref:fig-catch-streams-proj-nextyr-fr)", "(ref:fig-catch-streams-proj-nextyr-en)")}
plot_ref_points_dist_mcmc(base_model, biomass_col = "B2023")
```

(ref:fig-catch-streams-proj-nextnextyr-en) Projected `r base_model$dat$end.yr + 3` relative spawning biomass for catch occurring in `r base_model$dat$end.yr + 2`. Black points are medians of the posterior, thick lines are the 50% CI (25%--75%), and thin lines are the 95% CI (2.5%--97.5%). The solid red line is the LRP, $0.2B_0$, the dotted blue line is the $0.35B_0$ line, and the dashed green line is the USR, $0.4B_0$.

(ref:fig-catch-streams-proj-nextnextyr-fr) Biomasse reproductrice relative projetée `r base_model$dat$end.yr + 3` pour les captures effectuées dans `r base_model$dat$end.yr + 2`. Les points noirs sont les médianes du postérieur, les lignes épaisses sont l'IC à 50 % (25 %--75 %) et les lignes fines sont l'IC à 95 % (2,5 %--97,5 %). La ligne rouge continue est la LRP, $0,2B_0$, la ligne bleue pointillée est la ligne $0,35B_0$, et la ligne verte pointillée est l'USR, $0,4B_0$.

```{r fig-catch-streams-nextnextyr-proj, fig.cap = ifelse(fr(), "(ref:fig-catch-streams-proj-nextnextyr-fr)", "(ref:fig-catch-streams-proj-nextnextyr-en)")}
plot_ref_points_dist_mcmc(base_model, biomass_col = "B2024")
```

(ref:fig-catch-streams-proj-nextnextnextyr-en) Projected `r base_model$dat$end.yr + 4` relative spawning biomass for catch occurring in `r base_model$dat$end.yr + 3`. Black points are medians of the posterior, thick lines are the 50% CI (25%--75%), and thin lines are the 95% CI (2.5%--97.5%). The solid red line is the LRP, $0.2B_0$, the dotted blue line is the $0.35B_0$ line, and the dashed green line is the USR, $0.4B_0$.

(ref:fig-catch-streams-proj-nextnextnextyr-fr) Biomasse reproductrice relative projetée `r base_model$dat$end.yr + 4` pour les captures effectuées en `r base_model$dat$end.yr + 3`. Les points noirs sont les médianes du postérieur, les lignes épaisses sont l'IC à 50 % (25 %--75 %), et les lignes fines sont l'IC à 95 % (2,5 %--97,5 %). La ligne rouge continue est la LRP, $0,2B_0$, la ligne bleue pointillée est la ligne $0,35B_0$, et la ligne verte pointillée est l'USR, $0,4B_0$.

```{r fig-catch-streams-nextnextnextyr-proj, fig.cap = ifelse(fr(), "(ref:fig-catch-streams-proj-nextnextnextyr-fr)", "(ref:fig-catch-streams-proj-nextnextnextyr-en)")}
plot_ref_points_dist_mcmc(base_model, biomass_col = "B2025")
```

(ref:fig-catch-streams-proj-nextnextnextnextyr-en) Projected `r base_model$dat$end.yr + 5` relative spawning biomass for catch occurring in `r base_model$dat$end.yr + 4`. Black points are medians of the posterior, thick lines are the 50% CI (25%--75%), and thin lines are the 95% CI (2.5%--97.5%). The solid red line is the LRP, $0.2B_0$, the dotted blue line is the $0.35B_0$ line, and the dashed green line is the USR, $0.4B_0$.

(ref:fig-catch-streams-proj-nextnextnextnextyr-fr) Biomasse reproductrice relative projetée `r base_model$dat$end.yr + 5` pour les captures effectuées en `r base_model$dat$end.yr + 4`. Les points noirs sont les médianes du postérieur, les lignes épaisses sont l'IC à 50 % (25 %--75 %), et les lignes fines sont l'IC à 95 % (2,5 %--97,5 %). La ligne rouge continue est la LRP, $0,2B_0$, la ligne bleue pointillée est la ligne $0,35B_0$, et la ligne verte pointillée est l'USR, $0,4B_0$.

```{r fig-catch-streams-nextnextnextnextyr-proj, fig.cap = ifelse(fr(), "(ref:fig-catch-streams-proj-nextnextnextnextyr-fr)", "(ref:fig-catch-streams-proj-nextnextnextnextyr-en)")}
plot_ref_points_dist_mcmc(base_model, biomass_col = "B2026")
```
