
```{r appendix-data-para-1-en, eval = !fr(), results = 'asis'}
cat("# BIOLOGICAL DATA APPENDIX {#app:bio-data-appendix}
This appendix summarizes the biological data for `r sp` in `r bc`. The length and age compositions collected from both surveys and commercial sources are illustrated (Figures \@ref(fig:fig-lengths) and \@ref(fig:fig-ages)); however, all biological parameters were estimated from synoptic survey data only. The values used in the assessment (Table \@ref(tab:growth-params-table)) were aggregated from the four synoptic surveys that are each run biennially off the West coast of `r bc`: the `r qcs`, the `r hss`, the `r wcvis`, and the `r wchgs`.")
```

```{r appendix-data-para-1-fr, eval = fr(), results = 'asis', needs_trans = TRUE}
<<appendix-data-para-1-en>>
```

```{r appendix-data-para-2-en, eval = !fr(), results = 'asis'}
cat("## LENGTH AND WEIGHT MODEL {#length-weight-model}
All valid length/weight pairs of data were extracted based on the criteria shown in table A.1. The length-weight equation used was:
\begin{equation}
  W_s = \alpha_s L_s^{\beta_s}
  (\#eq:length-weight)
\end{equation}
where $\alpha_s$ and $\beta_s$ are parameters for sex $s$ and $L_s$ and $W_s$ are paired length-weight observations.

We applied Eq. \@ref(eq:length-weight) to survey observations for the three synoptic surveys used in this assessment. Results are plotted for each survey individually, and together with data from the fourth survey `r wchgs` to represent PMFC areas 3CD and 5ABCDE combined as 'coastwide' (Figure \@ref(fig:fig-length-weight)).
    ")
```

```{r appendix-data-para-2-fr, eval = fr(), results = 'asis', needs_trans = TRUE}
<<appendix-data-para-2-en>>
```

```{r appendix-data-para-3-en, eval = !fr(), results = 'asis'}
cat("## VON-BERTALANFFY MODEL {#vonb-model}
We used the von-Bertalanffy function to estimate growth rates for `r sp`:
\begin{equation}
  L_s = L_{\infty_s}(1 - e^{-k_s (a_s - t_{0_s})})
  (\#eq:vonb)
\end{equation}
where $L_{\infty_s}$, $k_s$, and $t_{0_s}$ are parameters specific to sex $s$ and $L_s$ and $a_s$ are paired length-age observations.

We applied Eq. \@ref(eq:vonb) to survey observations for the three synoptic surveys used in this assessment. Results are plotted for each survey individually, and together with data from the fourth survey `r wchgs` to represent PMFC areas 3CD and 5ABCDE combined as 'coastwide' (Figure \@ref(fig:fig-vb)).
")
```

```{r appendix-data-para-3-fr, eval = fr(), results = 'asis', needs_trans = TRUE}
<<appendix-data-para-3-en>>
```

```{r appendix-data-para-4-en, eval = !fr(), results = 'asis'}
cat("## MATURITY-AT-AGE MODEL
The maturity-at-age model used for `r sp` estimates age-at-50% maturity ($a_{s_{50\%}}$) and standard deviation of age-at-50% maturity ($\sigma_{s_{50\%}}$) by applying the Limited-memory Broyden Fletcher Goldfarb Shanno algorithm with Bounds (L-BFGS-B) to minimize the sum-of-squares between the observed and expected proportion mature:
\begin{equation}
  P_{a_s} = \frac{1}{1 + e^{-\sigma_{s_{50\%}}(a_s-a_{s_{50\%}})}}
  (\#eq:mat-at-age)
\end{equation}
where $P_{a_s}$ is the observed proportion mature at age $a_s$ for sex $s$. 

The same equation can also be applied to lengths instead of ages. We applied Eq. \@ref(eq:mat-at-age) to survey observations of both age and length from the three synoptic surveys used in this assessment. Results are plotted for each survey individually, and together with data from the fourth survey `r wchgs` to represent PMFC areas 3CD and 5ABCDE combined as 'coastwide' (Figure \@ref(fig:fig-mat)).

\clearpage
## FIGURES
")
```

```{r appendix-data-para-4-fr, eval = fr(), results = 'asis', needs_trans = TRUE}
<<appendix-data-para-4-en>>
```

<!-- Length compositions: --------------------------------------------------------->

(ref:fig-lengths-en) Length-frequency plot where female fish are shown as red bars and male fish are shown behind as blue bars. The total number of fish measured for a given survey and year are indicated in the top left corner of each panel. Histograms are only shown if there are more than 20 fish measured for a given survey-year combination. 

(ref:fig-lengths-fr) Graphique de la fréquence selon la longueur où les poissons femelles sont représentés par des barres rouge et les poissons mâles sont représentés derrière par des barres bleu. Le nombre total de poissons mesurés pour un relevé et une année donnés est indiqué au coin supérieur gauche de chaque panneau. Les histogrammes ne sont présentés que s’il y a plus de 20 poissons mesurés pour une combinaison donnée de relevé et d’année. 
TODO: translate weighting description?

```{r fig-lengths, fig.cap = ifelse(fr(), "(ref:fig-lengths-fr)", "(ref:fig-lengths-en)"), fig.asp = 1, out.width = "6in"}

bin_width1 <- diff(quantile(length_samples_survey$length,
  na.rm = TRUE,
  probs = c(0, 1)
)) / 20

bin_width2 <- diff(quantile(length_samples_ft$length,
  na.rm = TRUE, probs = c(0, 1)
)) / 20

bin_width3 <- diff(quantile(length_samples_ss$length,
  na.rm = TRUE, probs = c(0, 1)
)) / 20

bin_width <- mean(c(bin_width1, bin_width2, bin_width3), na.rm = TRUE)

ss <- tidy_lengths_weighted(length_samples_survey,
  dat_survey_sets = dat$survey_sets,
  bin_size = bin_width,
  sample_type = "survey"
)

sf <- length_samples_ft %>%
  # mutate(sex = 2) %>% # fake all sex as female for commercial samples; often not sexed
  tidy_lengths_weighted(
    dat_catch = dat$catch,
    bin_size = bin_width,
    sample_type = "commercial", spp_cat_code = 1
  ) %>%
  mutate(
    survey_abbrev = "Freezer Trawlers"
  )

sc <- length_samples_ss %>%
  # mutate(sex = 2) %>% # fake all sex as female for commercial samples; often not sexed
  tidy_lengths_weighted(
    dat_catch = dat$catch,
    bin_size = bin_width,
    sample_type = "commercial", spp_cat_code = 1
  ) %>%
  mutate(
    survey_abbrev = "Shoreside"
  )

min_total <- 20

sc_old <- filter(sc, year < 1995) # are we interested in length frequencies pre-1980?
sc <- filter(sc, year > 1995)
sb <- suppressWarnings(bind_rows(ss, sc, sf))
sb$survey_abbrev <- factor(sb$survey_abbrev,
  levels = c(
    "SYN WCHG", "SYN HS", "SYN QCS", "SYN WCVI",
    tr("Freezer Trawlers"), tr("Shoreside")
  )
)
sb$year <- factor(sb$year, levels = seq(1996, 2021))

g_lengths <- plot_lengths(sb,
  fill_col = c("M" = "#0096FF10", "F" = "#FF000010"),
  line_col = c("M" = "#0000FF", "F" = "#FF0000"),
  survey_cols = NULL,
  # survey_cols = stats::setNames(
  #   c("#FC8D62", "#FC8D62", "#FC8D62", "#FC8D62", 
  #     "#0096FF", "#0096FF"),
  #     # "#4682B4", "#4682B4"),
  #   c(
  #     "SYN WCHG", "SYN HS", "SYN QCS", "SYN WCVI",
  #     tr("Freezer Trawlers"),
  #     tr("Shoreside")
  # )
  # ),
  bin_size = bin_width, min_total = min_total
) +
  # scale_x_continuous(breaks = x_breaks, labels = x_labels) +
  guides(colour = "none", fill = "none") +
  ggtitle("") +
  ggplot2::xlab(paste(tr("Length"), "(cm)")) +
  ggplot2::ylab(tr("Relative length frequency"))

g_lengths
```

<!-- Age composition --------------------------------------------------------->

(ref:fig-ages-en) Example age-frequency plot. Female fish are shown as
red circles and male fish are shown behind as blue
circles. The total number of fish aged for a given survey or fishery and year are
indicated along the top of the panels. Diagonal lines are shown at five-year
intervals to facilitate tracing cohorts through time. 

(ref:fig-ages-fr) Exemple de graphique de la fréquence selon l’âge. Les poissons femelles sont représentés par des cercles rouge, et les poissons mâles sont représentés derrière par des cercles bleu. Le nombre total de poissons dont l’âge a été déterminé pour un relevé ou une pêcherie et une année donnés est indiqué en haut des panneaux. Les lignes diagonales sont représentées à des intervalles de cinq ans pour faciliter le suivi des cohortes au fl du temps.
TODO translate weighting

```{r fig-ages, fig.cap = ifelse(fr(), "(ref:fig-ages-fr)", "(ref:fig-ages-en)"), fig.asp = 1, out.width = "6in"}

ss <- tidy_ages_weighted(dat$survey_samples, dat_survey_sets = dat$survey_sets,
  sample_type = "survey"
)

ss$survey_abbrev <- factor(ss$survey_abbrev)
s_ages <- plot_ages(ss,
  line_col = c("M" = "#0000FF", "F" = "#FF0000"),
  survey_cols = NULL
  # survey_cols = stats::setNames(
  #   c("#FC8D62", "#FC8D62", "#FC8D62", "#FC8D62"),
  #   c("SYN WCHG", "SYN HS", "SYN QCS", "SYN WCVI")
  # )
) +
  facet_wrap(~survey_abbrev, nrow = 1, scales = "free_x") +
  guides(fill = "none", colour = "none") +
  theme(
    plot.title = element_blank(),
    axis.title = element_blank()
  )


sc <- tidy_ages_weighted(comm_ss, dat_catch = dat$catch,
  sample_type = "commercial"
) %>% mutate(
  survey_abbrev = "Shoreside"
)

sf <- tidy_ages_weighted(comm_ft, dat_catch = dat$catch,
  sample_type = "commercial"
) %>% mutate(
  survey_abbrev = "Freezer Trawlers"
)

sb <- suppressWarnings(bind_rows(sc, sf))

sb$survey_abbrev <- factor(sb$survey_abbrev)

c_ages <- plot_ages(sb,
  line_col = c("M" = "#0000FF", "F" = "#FF0000"),
  survey_cols = NULL
  # survey_cols = stats::setNames(
  #   # c("black", "black"), 
  #   c("#0096FF", "#0096FF"),
  #   c("Freezer Trawlers", "Shoreside"))
) +
  guides(fill = "none", colour = "none") +
  theme(
    plot.title = element_blank(),
    axis.title = element_blank()
  )

grid.arrange(s_ages, c_ages,
  nrow = 2,
  # heights = c(1.1,1),
  left = tr("Ages (years)"),
  bottom = tr("Year sampled")
)
```

<!-- Length/weight ----------------------------------------------------------->

(ref:fig-length-weight-en) Length/weight fits by sex. 
The length-weight curve is of the form $\log (W_i) \sim$ Student-t $(df = 3, \log(a) + b \log(L_i), \sigma),$ with $W_i$ and $L_i$ representing the weight and length for fish $i$ and $\sigma$ representing the observation error scale. The degrees of freedom of the Student-t distribution is set to 3 to be robust to outliers. The variables $a$ and $b$ represent the estimated length-weight parameters. Female model fits are indicated as solid red lines and male model fits are indicated as blue lines. Text on the panels shows the parameter estimates and open circles represent individual fish that the models are fit to. These figures include all survey samples.

(ref:fig-length-weight-fr) Ajustement du modèle pour le poids en fonction de la longueur et du sexe. 
La courbe de croissance de la longueur selon le poids est de la forme $\log (W_i) \sim$ Student-t $(df = 3, \log(a) + b \log(L_i), \sigma),$, où $W_i$ et $L_i$ représentent le poids et la longueur pour les poissons i et σ représente l’échelle des erreurs d’observation. Nous avons fxé les degrés de liberté de la distribution de Student t à 3 pour conférer une certaine robustesse par rapport aux valeurs aberrantes. Les variables a et b représentent les paramètres de la longueur selon le poids estimés. Les ajustements du modèle pour les femelles sont indiqués par des lignes pleines rouge, et les ajustements du modèle pour les mâles sont indiqués par des lignes bleu tiretées. Le texte sur les panneaux montre les estimations des paramètres, et les cercles ouverts représentent les poissons individuels auxquels les modèles sont ajustés.

```{r fig-length-weight, fig.cap = ifelse(fr(), "(ref:fig-length-weight-fr)", "(ref:fig-length-weight-en)"), out.width = "6in"}

if(!exists("data_dir")){
  stop("`data_dir` does not exist. If running from command line, ",
       "source('index.Rmd') to set up all project variables", call. = FALSE)
}
lw_fn <- file.path(data_dir, "fit_lw_output.rds")
if(file.exists(lw_fn)){
  lw_lst <- readRDS(lw_fn)  
}else{
  lw_lst <- list(
    fit_length_weight(filter(survey_samples, survey_abbrev %in% "SYN QCS"), sex = "female"),
    fit_length_weight(filter(survey_samples, survey_abbrev %in% "SYN QCS"), sex = "male"),
    fit_length_weight(filter(survey_samples, survey_abbrev %in% "SYN HS"), sex = "female"),
    fit_length_weight(filter(survey_samples, survey_abbrev %in% "SYN HS"), sex = "male"),
    fit_length_weight(filter(survey_samples, survey_abbrev %in% "SYN WCVI"), sex = "female"),
    fit_length_weight(filter(survey_samples, survey_abbrev %in% "SYN WCVI"), sex = "male"),
    fit_length_weight(survey_samples_syn, sex = "female"),
    fit_length_weight(survey_samples_syn, sex = "male"))
  saveRDS(lw_lst, lw_fn)
}
lw_title_lst <- list(
  tr("SYN QCS (5AB)"),
  tr("SYN HS (5CD)"),
  tr("SYN WCVI (3CD)"),
  tr("Coastwide"))

plot_lw_panels <- function(lw_f, lw_m){
  plot_length_weight(object_female = lw_f,
                     object_male = lw_m,
                     col = c("Female" = "#FF0000", "Male" = "#0000FF"),
                     #pts_col = TRUE,
                     french = fr()) +
    guides(colour = "none", fill = "none", lty = "none") +
    
    # coord_cartesian(xlim = c(0, 85), ylim = c(0, 6.7)) +
    xlim(0, 85) +
    theme(axis.title = element_blank())
}

lw_plot_lst <- list(
  plot_lw_panels(lw_lst[[1]], lw_lst[[2]]) +
  ggtitle(lw_title_lst[[1]]),
  
  plot_lw_panels(lw_lst[[3]], lw_lst[[4]]) +
  ggtitle(lw_title_lst[[2]]),
  
  plot_lw_panels(lw_lst[[5]], lw_lst[[6]]) +
  ggtitle(lw_title_lst[[3]]),

  plot_lw_panels(lw_lst[[7]], lw_lst[[8]]) +
  ggtitle(lw_title_lst[[4]]))

grid.arrange(grobs = lw_plot_lst,
             ncol = 2,
             bottom = paste0(tr("Length"), " (cm)"),
             left = tr("Weight (kg)"))

```


<!-- Growth ------------------------------------------------------------------>

(ref:fig-vb-en) The length-age growth curve is a von-Bertalanffy model of the form $L_i \sim \operatorname{Log-normal} \left( \log(l_\mathrm{inf} (1 - \exp(-k (A_i - t_0)))), \sigma \right)$ where $L_i$ and $A_i$ represent the length and age of fish $i$, $l_\mathrm{inf}$, $k$, and $t_0$ represent the von-Bertalanffy growth parameters, and $\sigma$ represents the scale parameter. Female model fits are indicated as solid red lines and male model fits are indicated as dashed blue lines. Text on the panels shows the parameter estimates and open circles represent individual fish that the models are fit to. 

<!-- These figures include all survey samples.  -->
<!-- `r base_model$dat$start.yr` to `r base_model$dat$end.yr` for `r sp`.  -->

(ref:fig-vb-fr) TODO

```{r fig-vb, fig.cap = ifelse(fr(), "(ref:fig-vb-fr)", "(ref:fig-vb-en)"), fig.asp = 1.2, out.width = "6in"}

if(!exists("data_dir")){
  stop("`data_dir` does not exist. If running from command line, ",
       "source('index.Rmd') to set up all project variables", call. = FALSE)
}

commercial_samples2 <- filter(commercial_samples, age < 40)

vb_fn <- file.path(data_dir, "fit_vb_output_w_comm.rds")
if(file.exists(vb_fn)){
  vb_lst <- readRDS(vb_fn)
}else{
  vb_lst <- list(
    fit_vb(filter(survey_samples, survey_abbrev %in% "SYN QCS")),
    fit_vb(filter(survey_samples, survey_abbrev %in% "SYN QCS"), sex = "male"),
    fit_vb(filter(survey_samples, survey_abbrev %in% "SYN HS")),
    fit_vb(filter(survey_samples, survey_abbrev %in% "SYN HS"), sex = "male"),
    fit_vb(filter(survey_samples, survey_abbrev %in% "SYN WCVI")),
    fit_vb(filter(survey_samples, survey_abbrev %in% "SYN WCVI"), sex = "male"),
    fit_vb(survey_samples_syn),
    fit_vb(survey_samples_syn, sex = "male"),
    fit_vb(commercial_samples2),
    fit_vb(commercial_samples2, sex = "male"),
    fit_vb(all_age_samples),
    fit_vb(all_age_samples, sex = "male"))
  saveRDS(vb_lst, vb_fn)
}
vb_title_lst <- list(
  tr("SYN QCS (5AB)"),
  tr("SYN HS (5CD)"),
  tr("SYN WCVI (3CD)"),
  tr("Coastwide synoptic"),
  tr("All commercial samples"),
  tr("All samples"))

plot_vb_panels <- function(vb_f, vb_m){
  plot_vb(object_female = vb_f,
          object_male = vb_m,
          col = c("Female" = "#FF0000", "Male" = "#0000FF"),
          #pts_col = TRUE,
          french = fr()) +
    guides(colour = "none", fill = "none", lty = "none") +
    theme(axis.title = element_blank()) +
    coord_cartesian(xlim = c(0, 28), ylim = c(0, 75))
}

vb_plot_lst <- list(
  plot_vb_panels(vb_lst[[1]], vb_lst[[2]]) +
  ggtitle(vb_title_lst[[1]]),
  
  plot_vb_panels(vb_lst[[3]], vb_lst[[4]]) +
  ggtitle(vb_title_lst[[2]]),
  
  plot_vb_panels(vb_lst[[5]], vb_lst[[6]]) +
  ggtitle(vb_title_lst[[3]]),
  
  plot_vb_panels(vb_lst[[7]], vb_lst[[8]]) +
  ggtitle(vb_title_lst[[4]]),
  
  plot_vb_panels(vb_lst[[9]], vb_lst[[10]]) +
  ggtitle(vb_title_lst[[5]]),
  
  plot_vb_panels(vb_lst[[11]], vb_lst[[12]]) +
  ggtitle(vb_title_lst[[6]]))

grid.arrange(grobs = vb_plot_lst,
             ncol = 2,
             left = paste0(tr("Length"), " (cm)"),
             bottom = tr("Age (years)"))
```

<!-- Maturity ---------------------------------------------------------------->

```{r calc-maturities}
# mat_model <- function(par, age, prop_mature) {
#   prop_m <- 1 / (1 + exp(-(age - par[1]) / par[2]))
#   sum((prop_m - prop_mature)^2) # sum of squares
# }

mat_model <- function(par, age, prop_mature){
  prop_m <- plogis(age, par[1], par[2])
  sum((prop_m - prop_mature) ^ 2)
}


save_ogive_dataframe <- function(data, maturities_kept) {
 
  matlst <- list()
  obj <- list()
  for (sex in 1:2) {

    matlst[[sex]] <- data[!duplicated(data$specimen_id), , drop = FALSE] %>%
      filter(maturity_code %in% maturities_kept,
             maturity_convention_code != 9) %>%
      filter(sex == !!sex) %>%
      filter(!is.na(age)) %>%
      group_by(age) %>%
      mutate(is_mature = ifelse(maturity_code < 3, FALSE, TRUE)) %>%
      summarize(prop_mature = sum(is_mature) / n()) %>%
      ungroup()

    obj[[sex]] <- optim(
      par = c(6, 1),
      fn = mat_model,
      method = "L-BFGS-B",
      lower = 0.00,
      upper = Inf,
      age = matlst[[sex]]$age,
      prop_mature = matlst[[sex]]$prop_mature
    )

    matlst[[sex]]$sex <- sex
    matlst[[sex]]$age50mat <- round(obj[[sex]]$par[1], 2)
    matlst[[sex]]$sd50mat <- round(obj[[sex]]$par[2], 2)
    matlst[[sex]]
  }
  df <- do.call("rbind", matlst)

  df$data <- deparse(substitute(data))
  df$maturities_kept <- paste0(deparse(maturities_kept))
  df
}

`Synoptic only` <- survey_samples_syn %>% filter(age < 41)
`All samples` <- all_age_samples

d1 <- save_ogive_dataframe(`Synoptic only`,
  maturities_kept = c(1, 2, 3, 4, 5, 6, 7)
)
d2 <- save_ogive_dataframe(`All samples`,
  maturities_kept = c(1, 2, 3, 4, 5, 6, 7)
)
d3 <- save_ogive_dataframe(`All samples`,
  maturities_kept = c(1, 2, 3, 4, 5, 6)
)
d4 <- save_ogive_dataframe(`All samples`,
  maturities_kept = c(1, 4, 5, 6)
)
# d5 <- save_ogive_dataframe(`Synoptic only`,
#   maturities_kept = c(1, 4, 5, 6)
# )

mat_dat <- bind_rows(d1, d2, d3, d4) %>% mutate(
  model = case_when(
    maturities_kept == paste0(deparse(c(1, 2, 3, 4, 5, 6, 7))) ~ paste(data),
    maturities_kept == paste0(deparse(c(1, 2, 3, 4, 5, 6))) ~ paste(data, "\n(resting removed)"),
    maturities_kept == paste0(deparse(c(1, 4, 5, 6))) ~ paste(data, "\n(maturing, developing \nand resting removed)")
    # maturities_kept == paste0(deparse(c(1, 2, 3, 4, 5, 6))) ~ "Resting removed",
    # maturities_kept == paste0(deparse(c(1, 4, 5, 6))) ~ "Maturing, developing \nand resting removed"
  ),
  sex = ifelse(sex == 1L, "Male", "Female")
)
unique(mat_dat$model)
mat_dat$model <- factor(mat_dat$model, levels = c(
  "Synoptic only",
  "All samples",
  "All samples \n(resting removed)",
  "All samples \n(maturing, developing \nand resting removed)"
  # "Resting removed",
  # "Maturing, developing \nand resting removed"
  # "Synoptic only \n(maturing, developing \nand resting removed)"
), labels = c(
  "Synoptic only",
  "All samples",
  # "All samples \n(resting removed)",
  # "All samples \n(maturing, developing \nand resting removed)"
  "Resting removed",
  "Maturing, developing \nand resting removed"
  # "Synoptic only \n(maturing, developing \nand resting removed)"
))

```


(ref:fig-mat-en) Age-at-maturity ogive plots. Maturity ogives are logistic curves fit to the proportion of fish at each age that were categorized as mature vs. not mature. The dashed vertical lines indicate the estimated age at 50% maturity. Models are fit to all available samples regardless of time of year. The ogives used in the base model  were based only on synoptic survey samples (male age at 50% maturity = `r mat_dat[mat_dat$model == "Synoptic only" & mat_dat$sex == "Male", ]$age50mat[1]`, female age at 50% maturity = `r mat_dat[mat_dat$model == "Synoptic only" & mat_dat$sex == "Female", ]$age50mat[1]`). Including all other survey and commercial samples ('All samples') doesn't not change the shape of the ogive, but we use this slightly larger dataset to check the influence of removing macroscopic maturity classifications that may be prone to misclassification and/or have uncertainty in their relationship with functional maturity ('Resting removed' and 'Maturing, developing and resting removed'). Maturing, developing and resting removed had the best fit to the data (male age at 50% maturity = `r mat_dat[mat_dat$model == "Maturing, developing \nand resting removed" & mat_dat$sex == "Male", ]$age50mat[1]`, female age at 50% maturity = `r mat_dat[mat_dat$model == "Maturing, developing \nand resting removed" & mat_dat$sex == "Female", ]$age50mat[1]`). 
These values were used as a sensitivity run.
<!-- However, we used the ogive with resting removed as our sensitivity run as it represented the most extreme alternative reality supported by the data (male age at 50% maturity = `r mat_dat[mat_dat$model == "Resting removed" & mat_dat$sex == "Male", ]$age50mat[1]`, female age at 50% maturity = `r mat_dat[mat_dat$model == "Resting removed" & mat_dat$sex == "Female", ]$age50mat[1]`). -->

<!-- `r base_model$dat$start.yr` to `r base_model$dat$end.yr` for `r sp`.  -->

(ref:fig-mat-fr) L’âge-à-maturité pour les courbes de fréquences cumulées. TODO: the rest of translation.

```{r fig-mat, fig.cap = ifelse(fr(), "(ref:fig-mat-fr)", "(ref:fig-mat-en)"), fig.asp = 0.5, out.width = "6in"}
# library(RColorBrewer)
# library(patchwork)
# female_cols <- RColorBrewer::brewer.pal(n = 6, name = "Reds")
female_cols <- RColorBrewer::brewer.pal(n = 8, name = "YlOrRd")
female_cols <- female_cols[4:7]
female_cols <- rev(female_cols)

# male_cols <- RColorBrewer::brewer.pal(n = 6, name = "Blues")
male_cols <- RColorBrewer::brewer.pal(n = 9, name = "YlGnBu")
male_cols <- male_cols[4:8]
male_cols <- rev(male_cols)


plot_bridging_mat_ogives <- function(mat_dat,
                                     plot_sex = "Female",
                                     col_vec = female_cols,
                                     ogive_size = 1.3,
                                     ogive_alpha = 0.4) {

  models <- unique(mat_dat$model)

  p <- mat_dat %>%
    filter(sex == !!plot_sex) %>%
    ggplot() +
    geom_point(aes(age, prop_mature, colour = model),
      # shape = 1,
      alpha = 0.7
    ) +
    scale_color_manual(values = col_vec, name = "Model") +
    ylab("Proportion mature") +
    xlab("Age") +
    ggtitle(plot_sex) +
    ggsidekick::theme_sleek()


  add_ogive <- function(p, i){
  p + geom_function(
    data = NULL,
    size = ogive_size,
    alpha = ogive_alpha,
    # lty="dashed",
    fun = function(x) {
      plogis(
        x,
        mat_dat[mat_dat$model == models[i] & mat_dat$sex == plot_sex, ]$age50mat[1],
        mat_dat[mat_dat$model == models[i] & mat_dat$sex == plot_sex, ]$sd50mat[1]
      )
    }, colour = col_vec[i], inherit.aes = FALSE
  ) +
    geom_vline(
      data = NULL,
      size = ogive_size / 2, lty = "dashed", alpha = ogive_alpha, xintercept =
        mat_dat[mat_dat$model == models[i] &
                  mat_dat$sex == plot_sex, ]$age50mat[1], colour = col_vec[i]
    )
    }

  for (i in seq_along(models)){
    p <- p %>% add_ogive(i)
  }

  p + coord_cartesian(expand = F, xlim = c(0, 26))
}

p1 <- plot_bridging_mat_ogives(mat_dat, plot_sex = "Male", col_vec = male_cols) + theme(
  legend.title = element_blank(),
  axis.title.x = element_blank(),
  legend.position = c(0.7, 0.25))
p2 <- plot_bridging_mat_ogives(mat_dat, plot_sex = "Female", col_vec = female_cols) +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
  legend.title = element_blank(),
  axis.title.x = element_blank(),
  legend.position = c(0.7, 0.25))

xlab <- ggplot(data.frame(l = "Age", x = 13, y = 1)) +
  geom_text(aes(x, y, label = l))+
  theme_void()


# (p1 + p2 )/xlab +
#   patchwork::plot_layout(heights = c(20, 1.5)) & coord_cartesian(expand = F, xlim = c(0, 26)) & theme(
#   legend.title = element_blank(),
#   axis.title.x = element_blank(),
#   legend.position = c(0.7, 0.25)
# )

grid.arrange(grobs = list(p1, p2),
             ncol = 2,
             # left = paste0(tr("Length"), " (cm)"),
             bottom = tr("Age (years)"))

```

\pagebreak

```{r appendix-data-para-5-en, eval = !fr(), results = 'asis'}
cat("## TABLES
")
```

```{r appendix-data-para-5-fr, eval = fr(), results = 'asis', needs_trans = TRUE}
<<appendix-data-para-5-en>>
```

```{r growth-params-table, results = "asis"}
cap <- paste0("Growth parameters estimated outside the ", iscam, " model. All parameters were estimated using samples from the four synoptic surveys, and were filtered to include areas 3CD and 5ABCDE only. For the age-at-50\\% maturity estimates, the following values were used to further filter the data: maturity\\_convention\\_code = 4 (flatfish), maturity\\_code = 5 (Male - Spawning, testes large, white and sperm evident), (Female - Ripe, ovaries containing entirely translucent, mature ova. eggs loose and will run from oviducts under slight pressure), and usability codes = 0 (Unknown), 1 (Fully usable), 2 (Fail, but all data usable), 6 (Gear torn, all data ok).")
if(fr()){
  cap <- paste0("Paramètres de croissance estimés en dehors du modèle ", iscam, ".")
}

table_growth_params(base_model,
                    digits = 3,
                    alpha_digits = 7,
                    caption = cap)

```

