# Figures

(ref:fig-catch-en) Commercial catch of `r sp` by area.

(ref:fig-catch-fr) Captures commerciales de `r en2fr(sp)` par zone.

```{r fig-catch, fig.cap = ifelse(fr(), "(ref:fig-catch-fr)", "(ref:fig-catch-en)")}
plot_catch(catch, french = fr())
```

(ref:fig-base-sb-en) Spawning biomass of `r sp` for the base model. The
solid black line is the median of the posteriors, the shaded ribbon
encapsulated by dotted lines covers the 95% Credible interval for the
posteriors, the point at $B_0$ is the median estimate for the unfished
biomass, and the vertical line over that point is the 95% Credible interval
for that parameter.

(ref:fig-base-sb-fr) Biomasse de frai de `r en2fr(sp)` pour le modèle de base.
Le site ligne noire pleine est la médiane des postérieures, le ruban ombragé
encapsulé par des lignes pointillées couvre l'intervalle crédible à 95% pour
les le point à $B_0$ est l'estimation médiane de la biomasse non pêchée, et la
ligne verticale sur ce point est l'intervalle crédible à 95% pour les biomasse
non pêchée, et la ligne verticale au-dessus de ce point est l'intervalle
crédible à 95% pour ce paramètre.

```{r fig-base-sb, fig.cap = ifelse(fr(), "(ref:fig-base-sb-fr)", "(ref:fig-base-sb-en)")}
plot_biomass_mcmc(base_model, angle_x_labels = TRUE, text_title_size = NULL)
```

(ref:fig-base-recr-en) Recruitment of `r sp` for the base model. The
black points are the medians of the posteriors, the vertical black lines
are the 95% Credible intervals for the posteriors, the point at $R_0$
is the median estimate for the initial recruitment parameter $R_0$,
and the vertical line over that point and shaded ribbon across the time series
is the 95% Credible interval for that parameter.

(ref:fig-base-recr-fr) Recrutement de `r en2fr(sp)` pour le modèle de base.
Les points noirs de points noirs sont les médianes des postérieurs, les
lignes noires verticales sont les intervalles crédibles à 95 % pour les
valeurs postérieures, le point à $R_0$ est l'estimation médiane du paramètre
de recrutement initial $R_0$ est l'estimation médiane pour le paramètre de
recrutement initial $R_0$, et la ligne verticale sur ce point et le ruban
ombragé sur la série temporelle est l'intervalle crédible à 95% pour ce
paramètre.

```{r fig-base-recr, fig.cap = ifelse(fr(), "(ref:fig-base-recr-fr)", "(ref:fig-base-recr-en)")}
plot_recr_mcmc(base_model, angle_x_labels = TRUE, text_title_size = NULL)
```

(ref:fig-base-priors-posts-en) Prior probability distributions used in the base model (blue shaded areas) overlaid with posterior distribution histograms. The solid red line is the mode of the prior distribution, the vertical solid black line is the mean of the prior, and the vertical dashed black lines represent one standard deviation from the mean. Plots that are entirely shaded blue show uniform priors which are shaded underneath the prior value.

(ref:fig-base-priors-posts-fr)  Distributions de probabilité antérieures utilisées dans le modèle de base (zones ombrées en bleu) superposées aux histogrammes de distribution postérieure. La ligne rouge pleine est le mode de la distribution antérieure, la ligne noire pleine verticale est la moyenne de la distribution antérieure, et les lignes noires pointillées verticales représentent un écart type de la moyenne. Les graphiques qui sont entièrement ombrés en bleu montrent des antériorités uniformes qui sont ombrées sous la valeur de l'antériorité.

```{r fig-base-priors-posts, fig.cap = ifelse(fr(), "(ref:fig-base-priors-posts-fr)", "(ref:fig-base-priors-posts-en)")}
plot_priors_posts_mcmc(base_model, text_title_size = NULL)
```

(ref:fig-base-trace-en) Trace plots for MCMC output of estimated lead parameters in the base model. The MCMC run has chain length `r f(mcmc_chain_length)` with a sample taken every `r f(mcmc_sample_freq)`^th^ iteration. Of the `r f(mcmc_num_samples)` samples taken, the first 1,000 were removed as a burn-in period. $q$ parameters represent catchability for the survey indices, with numerical indices representing: `r paste(base_index_gears$gear, " = ", base_index_gears$gear_name, collapse = ", ")`.

(ref:fig-base-trace-fr) Tracés pour la sortie MCMC des paramètres de plomb estimés dans le modèle de base. L'exécution MCMC a une longueur de chaîne `r f(mcmc_chain_length)` avec un échantillon pris chaque `r f(mcmc_sample_freq)`^ème^ itération. Parmi les `r f(mcmc_num_samples)` échantillons prélevés, les 1 000 premiers ont été retirés pour servir de période de rodage. Les paramètres $q$ représentent la capturabilité pour les indices de l'enquête, les indices numériques représentant : `r paste(base_index_gears$gear, " = ", base_index_gears$gear_name, collapse = ", ")`.

```{r fig-base-trace, fig.cap = ifelse(fr(), "(ref:fig-base-trace-fr)", "(ref:fig-base-trace-en)")}
plot_traces_mcmc(base_model,
                 plot_sel = FALSE, 
                 param_rm = c("m1", "m2", "rho", "vartheta", "ssb",
                              "msy1", "msy2", "fmsy1", "fmsy2", "umsy1", "umsy2",
                              "bmsy", "bo", "sbo"),
                 text_title_size = NULL)
```

(ref:fig-base-autocor-en) Autocorrelation plots for MCMC output of estimated lead parameters in the base model. See Figure \@ref(fig:fig-base-trace) for parameter descriptions.

(ref:fig-base-autocor-fr) Graphiques d'autocorrélation pour la sortie MCMC des paramètres de plomb estimés dans le modèle de base. Voir la figure \@ref(fig:fig-base-trace) pour la description des paramètres.

```{r fig-base-autocor, fig.cap = ifelse(fr(), "(ref:fig-base-autocor-fr)", "(ref:fig-base-autocor-en)")}
plot_autocor_mcmc(base_model, 
                  plot_sel = FALSE, 
                  param_rm = c("m1", "m2", "rho", "vartheta", "ssb",
                               "msy1", "msy2", "fmsy1", "fmsy2", "umsy1", "umsy2",
                               "bmsy", "bo", "sbo"),
                  text_title_size = NULL)
```

(ref:fig-base-trace-selex-en) Trace plots for MCMC output of estimated selectivity parameters in the base model. $\hat{a}$ are the estimates of selectivity-at-age-50%, $\hat{\gamma}$ are the estimated standard deviations on selectivity-at-age-50%. The numerical indices on the two parameters represent: `r paste(base_all_gears$gear, " = ", base_all_gears$gear_name, collapse = ", ")`.

(ref:fig-base-trace-selex-fr) Tracés de la sortie MCMC des paramètres de sélectivité estimés dans le modèle de base. Les $\hat{a}$ sont les estimations de la sélectivité à l'âge de 50 %, les $\hat{\gamma}$ sont les écarts types estimés de la sélectivité à l'âge de 50 %. Les indices numériques sur les deux paramètres représentent : `r paste(base_all_gears$gear, " = ", base_all_gears$gear_name, collapse = ", ")`.

```{r fig-base-trace-selex, fig.cap = ifelse(fr(), "(ref:fig-base-trace-selex-fr)", "(ref:fig-base-trace-selex-en)")}
plot_traces_mcmc(base_model,
                 plot_sel = TRUE, 
                 param_rm = c("m1", "m2", "rho", "vartheta", "ssb",
                              "msy1", "msy2", "fmsy1", "fmsy2", "umsy1", "umsy2",
                              "bmsy", "bo", "sbo"),
                 text_title_size = NULL)
```

(ref:fig-base-autocor-selex-en) Autocorrelation plots for MCMC output of estimated selectivity parameters in the base model. See Figure \@ref(fig:fig-base-trace-selex) for parameter descriptions.

(ref:fig-base-autocor-selex-fr) Graphiques d'autocorrélation pour la sortie MCMC des paramètres de sélectivité estimés dans le modèle de base. Voir la figure \@ref(fig:fig-base-trace-selex) pour la description des paramètres.

```{r fig-base-autocor-selex, fig.cap = ifelse(fr(), "(ref:fig-base-autocor-selex-fr)", "(ref:fig-base-autocor-selex-en)")}
plot_autocor_mcmc(base_model, 
                  plot_sel = TRUE, 
                  param_rm = c("m1", "m2", "rho", "vartheta", "ssb",
                               "msy1", "msy2", "fmsy1", "fmsy2", "umsy1", "umsy2",
                               "bmsy", "bo", "sbo"),
                  text_title_size = NULL)
```

(ref:fig-base-pairs-en) Pairs plots for MCMC estimated parameters in the base model. The lines in the points plots in the lower triangular panels are linear models with shaded 95% confidence intervals. The line plots in the diagonal panels represent density of the parameter values, and the values in the upper triangular panels are the correlations between parameters with text size being directly proportional to the absolute value of those values. See Figure \@ref(fig:fig-base-trace) for parameter descriptions.

(ref:fig-base-pairs-fr) Diagrammes de paires pour les paramètres estimés par MCMC dans le modèle de base. Les lignes dans les tracés de points dans les panneaux triangulaires inférieurs sont des modèles linéaires avec des intervalles de confiance à 95% ombrés. Les tracés de lignes dans les panneaux diagonaux représentent la densité des valeurs des paramètres, et les valeurs dans les panneaux triangulaires supérieurs sont les corrélations entre les paramètres, la taille du texte étant directement proportionnelle à la valeur absolue de ces valeurs. Voir la figure \@ref(fig:fig-base-trace) pour la description des paramètres.

```{r fig-base-pairs, fig.cap = ifelse(fr(), "(ref:fig-base-pairs-fr)", "(ref:fig-base-pairs-en)")}
plot_pairs_mcmc(base_model,
                plot_sel = FALSE,
                param_rm = c("m1", "m2", "rho", "vartheta", "ssb",
                             "msy1", "msy2", "fmsy1", "fmsy2", "umsy1", "umsy2",
                             "bmsy", "bo", "sbo"),
                text_title_size = NULL)
```

(ref:fig-base-index-fits-en) Index fits for the base model. The light brown points and vertical lines show the index values and CVs; the black points show the medians of the posteriors; the black solid vertical lines show the 95% credible intervals for the posteriors. The two lines connecting points along the time series are only present for aesthetic value. The 2014 WCHG Synoptic index point is shown but was not included in the model.

(ref:fig-base-index-fits-fr) Ajustements de l'indice pour le modèle de base. Les points et les lignes verticales marron clair montrent les valeurs de l'indice et les CV ; les points noirs montrent les médianes des valeurs postérieures ; les lignes verticales pleines noires montrent les intervalles crédibles à 95% pour les valeurs postérieures. Les deux lignes reliant les points le long de la série chronologique ne sont présentes que pour des raisons esthétiques. Le point d'indice Synoptic WCHG de 2014 est indiqué mais n'a pas été inclus dans le modèle.

```{r fig-base-index-fits, fig.cap = ifelse(fr(), "(ref:fig-base-index-fits-fr)", "(ref:fig-base-index-fits-en)")}
plot_index_mcmc(base_model,
                type = "fits",
                surv_index = survey_index,
                leg_loc = NULL,
                text_title_size = NULL)
```

(ref:fig-base-index-resids-en) Index Log standardized residuals. The points are the median of the posteriors for the $\epsilon$ parameter in iSCAM. The vertical lines represent the 95% credible intervals for those posteriors.

(ref:fig-base-index-resids-fr) Indice Log des résidus normalisés. Les points représentent la médiane des valeurs postérieures pour le paramètre $\epsilon$ dans iSCAM. Les lignes verticales représentent les intervalles crédibles à 95 % pour ces valeurs postérieures.

```{r fig-base-index-resids, fig.cap = ifelse(fr(), "(ref:fig-base-index-resids-fr)", "(ref:fig-base-index-resids-en)")}
plot_index_mcmc(base_model,
                type = "resids",
                surv_index = survey_index,
                leg_loc = NULL,
                text_title_size = NULL)
```

(ref:fig-base-age-fits-ft-en) Age composition fits for each sex for the Freezer trawler fleet. The black dots with vertical bars are the age composition data points. The red points are the medians of the posteriors for each age. The red shaded area with dotted edge represents the 95% credible intervals. The solid red line that connects the median posterior points is shown for aesthetics.

(ref:fig-base-age-fits-ft-fr) French here

```{r fig-base-age-fits-ft, fig.cap = ifelse(fr(), "(ref:fig-base-age-fits-ft-fr)", "(ref:fig-base-age-fits-ft-en)")}
plot_age_fits_mcmc(base_model, gear = 1)
```

(ref:fig-base-age-resids-ft-en) Age composition log standardized residuals for each sex for the Freezer trawler fleet. The boxplots have boxes that range from the 25^th^ to 75^th^ percentiles. The whiskers extend to 1.5 x the Interquartile range (IRQ - distance between the first and third quartiles). Plus symbols are outliers from the range of 1.5 x IRQ.

(ref:fig-base-age-resids-ft-fr) French here

```{r fig-base-age-resids-ft, fig.cap = ifelse(fr(), "(ref:fig-base-age-resids-ft-fr)", "(ref:fig-base-age-resids-ft-en)")}
plot_age_fits_mcmc(base_model, gear = 1)
```





(ref:fig-base-age-fits-ss-firsthalf-en) Age composition fits for each sex for the Shoreside fleet from 1996--2007. The black dots with vertical bars are the age composition data points. The red points are the medians of the posteriors for each age. The red shaded area with dotted edge represents the 95% credible intervals. The solid red line that connects the median posterior points is shown for aesthetics.

(ref:fig-base-age-fits-ss-firsthalf-fr) French here

```{r fig-base-age-fits-firsthalf-ss, fig.cap = ifelse(fr(), "(ref:fig-base-age-fits-ss-firsthalf-fr)", "(ref:fig-base-age-fits-ss-firsthalf-en)")}
plot_age_fits_mcmc(base_model, gear = 2, yrs = 1996:2007)
```
(ref:fig-base-age-fits-ss-secondhalf-en) Age composition fits for each sex for the Shoreside fleet from 1996--2007. The black dots with vertical bars are the age composition data points. The red points are the medians of the posteriors for each age. The red shaded area with dotted edge represents the 95% credible intervals. The solid red line that connects the median posterior points is shown for aesthetics.

(ref:fig-base-age-fits-ss--secondhalf-fr) French here

```{r fig-base-age-fits--secondhalf-ss, fig.cap = ifelse(fr(), "(ref:fig-base-age-fits-ss--secondhalf-fr)", "(ref:fig-base-age-fits-ss--secondhalf-en)")}
plot_age_fits_mcmc(base_model, gear = 2, yrs = 2008:2022)
```
\clearpage