# Figures

(ref:fig-bridge-biomass) Maximum Posterior Density (MPD) estimates of spawning biomass for the 2015 base model, and models constructed from the base model with cumulative changes progressing toward a new, split-sex base model.

(ref:fig-bridge-biomass-french) French caption here

```{r bridge-biomass, fig.cap = ifelse(french, "(ref:fig-bridge-biomass-french)", "(ref:fig-bridge-biomass)"), out.width = "100%" , fig.pos="H"}
plot_ts_mpd(models$bridge_models, bridge_models_text, "rt") +
  coord_cartesian(ylim = c(0, 2.5))
plot_ts_mpd(models$bridge_models, bridge_models_text, "rt", rel = TRUE)
plot_ts_mpd(models$bridge_models, bridge_models_text, "sbt") #+
  #coord_cartesian(ylim = c(0, 1))
plot_ts_mpd(models$bridge_models, bridge_models_text, "sbt", rel = TRUE)
```

(ref:fig-catches-map-cap) Total coastwide catch of `r sp`, including both landings and
  discards. See Table XX for values.

(ref:fig-catches-cap-map-french) French caption here

```{r main-catches-map, fig.cap = ifelse(french, "(ref:fig-catches-cap-map-french)", "(ref:fig-catches-map-cap)"), out.width = "100%" , fig.pos="H"}
cpue_spatial_1996_pres <- cpue_spatial %>% filter(year %in% 2018)
plot_cpue_spatial(cpue_spatial_1996_pres, french = french, start_year = start_catch_yr) +
  theme(axis.text.x = element_text(angle = 0)) +
  ggtitle(NULL) +
  scale_x_continuous(breaks = seq(from = 1900, to = 2100, by = 5))
```

(ref:fig-catches-cap) Total coastwide catch of `r sp`, including both landings and
  discards. See Table XX for values.

(ref:fig-catches-cap-french) French caption here

```{r main-catches, fig.cap = ifelse(french, "(ref:fig-catches-cap-french)", "(ref:fig-catches-cap)"), out.width = "100%", fig.pos="H"}
ct <- tidy_catch(catch, areas = NULL)
plot_catch(ct, french = french, xlim = c(start_catch_yr, end_catch_yr)) +
  theme(axis.text.x = element_text(angle = 0)) +
  ggtitle(NULL) +
  scale_x_continuous(breaks = seq(from = 1900, to = 2100, by = 5))
```

(ref:fig-catches-by-area-cap) Total catch of `r sp` by area, including both landings and
  discards. See Table XX for values.

(ref:fig-catches-by-area-cap-french) French caption here

```{r main-catches-by-area, fig.cap = ifelse(french, "(ref:fig-catches-by-area-cap-french)", "(ref:fig-catches-by-area-cap)"), out.width = "100%", fig.pos="H"}
ct_areas <- tidy_catch(catch, areas = c("3[CD]+", "5[ABCDE]+"))
plot_catch(ct_areas, french = french, xlim = c(start_catch_yr, end_catch_yr)) +
  theme(axis.text.x = element_text(angle = 0)) +
  ggtitle(NULL) +
  scale_x_continuous(breaks = seq(from = 1900, to = 2100, by = 5))
```

(ref:fig-catches-by-area-fine-cap) Total catch of `r sp` by area, including both landings and
  discards. See Table XX for values.

(ref:fig-catches-by-area-fine-cap-french) French caption here

```{r main-catches-by-area-fine, fig.cap = ifelse(french, "(ref:fig-catches-by-area-fine-cap-french)", "(ref:fig-catches-by-area-fine-cap)"), out.width = "100%", fig.pos="H"}
ct_areas <- tidy_catch(catch, areas = c("3[CD]+", "5[AB]+", "5[CD]", "5[E]"))
plot_catch(ct_areas, french = french, xlim = c(start_catch_yr, end_catch_yr)) +
  theme(axis.text.x = element_text(angle = 0)) +
  ggtitle(NULL) +
  scale_x_continuous(breaks = seq(from = 1900, to = 2100, by = 5))
```

(ref:fig-age-comps-cap) Age composition data by sex for the Reference Case for the commercial trawl fishery. Top numbers represent the number of age samples. Diagonal lines represent cohorts born decadally (for figure clarity).

(ref:fig-age-comps-cap-french) French caption here

```{r age-comps, fig.cap = ifelse(french, "(ref:fig-age-comps-cap-french)", "(ref:fig-age-comps-cap)"), out.width = "100%", fig.pos="H"}
ac <- tidy_ages_raw(commercial_samples, sample_type = "commercial")
plot_ages(ac) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  ggtitle(NULL) +
  scale_x_continuous(breaks = seq(from = 1900, to = 2100, by = 1))
```

(ref:fig-age-comps-weighted-cap) Weighted age composition data by sex for the Reference Case for the commercial trawl fishery. Top numbers represent the number of age samples. Diagonal lines represent cohorts born decadally (for figure clarity).

(ref:fig-age-comps-weighted-cap-french) French caption here

```{r age-comps-weighted, fig.cap = ifelse(french, "(ref:fig-age-comps-weighted-cap-french)", "(ref:fig-age-comps-weighted-cap)"), out.width = "100%", fig.pos="H"}
ac <- tidy_ages_weighted(commercial_samples,
                         sample_type = "commercial",
                         dat_catch = catch,
                         month_fishing_starts = month_fishing_starts,
                         day_fishing_starts = day_fishing_starts)
plot_ages(ac) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  ggtitle(NULL) +
  scale_x_continuous(breaks = seq(from = 1900, to = 2100, by = 1))
```

(ref:fig-age-comps-weighted-surveys-cap) Weighted age composition data by sex for the Reference Case for the `r wcviss`, `r hsss`, and `r qcsss`. Top numbers represent the number of age samples. Diagonal lines represent cohorts born decadally (for figure clarity).

(ref:fig-age-comps-weighted-surveys-cap-french) French caption here

```{r age-comps-weighted-surveys, fig.cap = ifelse(french, "(ref:fig-age-comps-weighted-surveys-cap-french)", "(ref:fig-age-comps-weighted-surveys-cap)"), out.width = "100%", fig.pos="H"}
ac <- tidy_ages_weighted(survey_samples,
                         sample_type = "survey",
                         dat_survey_sets = survey_sets,
                         survey = c("SYN WCVI",
                                    "SYN HS",
                                    "SYN QCS"))
plot_ages(ac) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  ggtitle(NULL) +
  scale_x_continuous(breaks = seq(from = 1900, to = 2100, by = 2))


```

(ref:fig-length-comps-weighted-cap) Weighted length composition data by sex for the Reference Case for the commercial trawl fishery. Top numbers represent the number of age samples. Diagonal lines represent cohorts born decadally (for figure clarity).

(ref:fig-length-comps-weighted-cap-french) French caption here

```{r length-comps-weighted, fig.cap = ifelse(french, "(ref:fig-length-comps-weighted-cap-french)", "(ref:fig-length-comps-weighted-cap)"), out.width = "100%", fig.pos="H"}
lc <- tidy_lengths_weighted(commercial_samples, sample_type = "commercial", dat_catch = catch)
plot_lengths(lc) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  ggtitle(NULL) +
  scale_x_continuous(breaks = seq(from = 0, to = 100, by = 5)) +
  theme(strip.text.y = element_text(angle = 0))
```

(ref:fig-priors-cap) Prior probability distributions used in the Reference Case. Parameters $q_k$ represent gears where: k = 2 is the `r qcsss`, k = 3 is the `r hsmas`, k = 4 is the `r hsss`, and k = 5 is the `r wcviss`.

(ref:fig-priors-cap-french) French caption here

```{r priors, fig.cap = ifelse(french, "(ref:fig-priors-cap-french)", "(ref:fig-priors-cap)"), out.width = "100%", fig.pos = "H"}
#make.priors.posts.plot(base_model)
```

(ref:fig-priors-posts-cap) Prior probability distributions used in the Reference Case with comparative posterior histograms. Parameter $q_k$ represents gears as follows: $k=1$: commercial trawl; $k=2$: `r qcsss`: $k=3$; `r hsmas`: $k=4$; `r hsss`, and $k=5$; `r wcviss`. The dotted red lines are the MPD estimates from the Reference Case.

(ref:fig-priors-posts-cap-french) French caption here

```{r priors-posts, fig.cap = ifelse(french, "(ref:fig-priors-posts-cap-french)", "(ref:fig-priors-posts-cap)"), out.width = "100%", fig.pos = "H"}
#make.priors.posts.plot(base_model, priors.only = FALSE)
```

(ref:fig-traces-cap) Trace plots for MCMC output of estimated parameters in the Reference Case. The MCMC run had chain length `r mcmc_chain_length`, with a sample taken at every `r mcsave`th iteration. Of the `r tot_num_posts` samples saved, the first `r burnin` were removed as a burn-in period. Parameters $q_k$ (catchability), $\hat{a}_k$ (selectivity-at-age-50%), and $\hat{\gamma}_k$ (selectivity standard deviation-at-50%) represent gears as follows: $k=1$: commercial trawl; $k=2$: `r qcsss`: $k=3$; `r hsmas`: $k=4$; `r hsss`, and $k=5$; `r wcviss`. The `r hsmas` did not have estimates selectivity, so there are no $\hat{a}_3$ or $\hat{\gamma}_3$ parameters.

(ref:fig-traces-cap-french) French caption here

```{r traces, fig.cap = ifelse(french, "(ref:fig-traces-cap-french)", "(ref:fig-traces-cap)"), out.width = "100%", fig.pos = "H"}
#make.traces.plot(base_model)
```

(ref:fig-autocorr-cap) Autocorrelation plots for MCMC output of estimated parameters in the
Reference Case. See Figure \@ref(fig:traces) for parameter descriptions.

(ref:fig-autocorr-cap-french) French caption here

```{r autocorr, fig.cap = ifelse(french, "(ref:fig-autocorr-cap-french)", "(ref:fig-autocorr-cap)"), out.width = "100%", fig.pos = "H"}
#make.autocor.plot(base_model)
```

(ref:fig-pairs-cap) Pairs plots for MCMC output of estimated parameters in the Reference Case.
  See Figure \@ref(fig:traces) for parameter descriptions.

(ref:fig-pairs-cap-french) French caption here

```{r pairs, fig.cap = ifelse(french, "(ref:fig-pairs-cap-french)", "(ref:fig-pairs-cap)"), out.width = "100%", fig.pos = "H"}
#make.pairs.plot(base_model)
```



<!-- (ref:fig-cpue-cap) CPUE -->

<!-- (ref:fig-cpue-cap-french) French caption here -->

<!-- ```{r cpue, fig.cap = ifelse(french, "(ref:fig-cpue-cap-french)", "(ref:fig-cpue-cap)"), out.width = "100%", fig.pos = "H"} -->
<!-- cp <-  -->

<!-- ``` -->
