<!-- The following code should appear at the beginning of the first appendix.
After that, all subsequent sections will be turned into appendices. -->

`r if(knitr:::is_latex_output()) '\\Appendices'`

`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'`

```{r appendix-data-para-1-en, eval = !fr(), results = 'asis'}
cat("# Biological Data Appendix {#app:bio-data-appendix}
This appendix summarizes the biological data for `r sp`.")
```

```{r appendix-data-para-1-fr, eval = fr(), results = 'asis', needs_trans = TRUE}
<<appendix-data-para-1-en>>
```

<!-- Age composition -------------------------------------------------------------->

(ref:fig-ages-en) Example age-frequency plot. Female fish are shown as
coloured (or black) circles and male fish are shown behind as light grey
circles. The total number of fish aged for a given survey or fishery and year are
indicated along the top of the panels. Diagonal lines are shown at five-year
intervals to facilitate tracing cohorts through time. 
TODO explain weighting

(ref:fig-ages-fr) Exemple de graphique de la fréquence selon l’âge. Les poissons femelles sont représentés par des cercles colorés (ou noirs), et les poissons mâles sont représentés derrière par des cercles gris clair. Le nombre total de poissons dont l’âge a été déterminé pour un relevé ou une pêcherie et une année donnés est indiqué en haut des panneaux. Les lignes diagonales sont représentées à des intervalles de cinq ans pour faciliter le suivi des cohortes au fl du temps.
TODO translate weighting

```{r fig-ages, fig.cap = ifelse(fr(), "(ref:fig-ages-fr)", "(ref:fig-ages-en)"), fig.asp = 1, out.width = "6in"}

ss <- tidy_ages_weighted(dat$survey_samples, dat_survey_sets = dat$survey_sets,
  sample_type = "survey"
)

ss$survey_abbrev <- factor(ss$survey_abbrev)
s_ages <- plot_ages(ss,
  survey_cols = stats::setNames(
    c("#FC8D62", "#FC8D62", "#FC8D62", "#FC8D62"),
    c("SYN WCHG", "SYN HS", "SYN QCS", "SYN WCVI")
  )
) +
  facet_wrap(~survey_abbrev, nrow = 1, scales = "free_x") +
  guides(fill = "none", colour = "none") +
  theme(
    plot.title = element_blank(),
    axis.title = element_blank()
  )


sc <- tidy_ages_weighted(comm_ss, dat_catch = dat$catch,
  sample_type = "commercial"
) %>% mutate(
  survey_abbrev = "Shoreside"
)

sf <- tidy_ages_weighted(comm_ft, dat_catch = dat$catch,
  sample_type = "commercial"
) %>% mutate(
  survey_abbrev = "Freezer Trawlers"
)

sb <- suppressWarnings(bind_rows(sc, sf))

sb$survey_abbrev <- factor(sb$survey_abbrev)

c_ages <- plot_ages(sb,
  survey_cols = stats::setNames(c("black", "black"), c("Freezer Trawlers", "Shoreside"))
) +
  guides(fill = "none", colour = "none") +
  theme(
    plot.title = element_blank(),
    axis.title = element_blank()
  )

grid.arrange(s_ages, c_ages,
  nrow = 2,
  # heights = c(1.1,1),
  left = en2fr("Ages (years)", fr()),
  bottom = en2fr("Year sampled", fr())
)
```

<!-- Growth ------------------------------------------------------------------>

(ref:fig-vb-en) 
The length-age growth curve is a von-Bertalanffy model.
<!-- of the form $L_i \\sim \\operatorname{Log-normal} \\left( \\log(l_\\mathrm{inf} (1 - \\exp(-k (A_i - t_0)))), \\sigma \\right)$ where $L_i$ and $A_i$ represent the length and age of fish $i$, $l_\\mathrm{inf}$, $k$, and $t_0$ represent the von Bertalanffy growth parameters, and $\\sigma$ represents the scale parameter. -->
Female model fits are indicated as solid black lines and male model fits are indicated as dashed grey lines. 
Text on the panels shows the parameter estimates and open grey circles represent individual fish that the models are fit to. 
<!-- These figures include all survey samples.  -->
<!-- `r base_model$dat$start.yr` to `r base_model$dat$end.yr` for `r sp`.  -->

(ref:fig-vb-fr) TODO

```{r fig-vb, fig.cap = ifelse(fr(), "(ref:fig-vb-fr)", "(ref:fig-vb-en)"), out.width = "6in"}

if(!exists("data_dir")){
  stop("`data_dir` does not exist. If running from command line, ",
       "source('index.Rmd') to set up all project variables", call. = FALSE)
}
vb_fn <- file.path(data_dir, "fit_vb_output.rds")
if(file.exists(vb_fn)){
  vb_lst <- readRDS(vb_fn)  
}else{
  vb_lst <- list(
    fit_vb(filter(survey_samples, survey_abbrev %in% "SYN QCS")),
    fit_vb(filter(survey_samples, survey_abbrev %in% "SYN QCS"), sex = "male"),
    fit_vb(filter(survey_samples, survey_abbrev %in% "SYN HS")),
    fit_vb(filter(survey_samples, survey_abbrev %in% "SYN HS"), sex = "male"),
    fit_vb(filter(survey_samples, survey_abbrev %in% "SYN WCVI")),
    fit_vb(filter(survey_samples, survey_abbrev %in% "SYN WCVI"), sex = "male"),
    fit_vb(survey_samples_syn),
    fit_vb(survey_samples_syn, sex = "male"))
  saveRDS(vb_lst, vb_fn)
}
vb_title_lst <- list(
  en2fr("SYN QCS (5AB)", fr()),
  en2fr("SYN HS (5CD)", fr()),
  en2fr("SYN WCVI (3CD)", fr()),
  en2fr("Coastwide", fr()))

plot_vb_panels <- function(vb_f, vb_m){
  plot_vb(object_female = vb_f,
          object_male = vb_m,
          french = fr()) +
    guides(colour = "none", fill = "none", lty = "none") +
    theme(axis.title = element_blank()) +
    coord_cartesian(xlim = c(0, 25), ylim = c(0, 75))
}

vb_plot_lst <- list(
  plot_vb_panels(vb_lst[[1]], vb_lst[[2]]) +
  ggtitle(vb_title_lst[[1]]),
  
  plot_vb_panels(vb_lst[[3]], vb_lst[[4]]) +
  ggtitle(vb_title_lst[[2]]),
  
  plot_vb_panels(vb_lst[[5]], vb_lst[[6]]) +
  ggtitle(vb_title_lst[[3]]),

  plot_vb_panels(vb_lst[[7]], vb_lst[[8]]) +
  ggtitle(vb_title_lst[[4]]))

grid.arrange(grobs = vb_plot_lst,
             ncol = 2,
             left = paste0(en2fr("Length", fr()), " (cm)"),
             bottom = en2fr("Age (years)", fr()))
```

<!-- Maturity ---------------------------------------------------------------->

(ref:fig-mat-en) Age- and length-at-maturity ogive plots. Maturity ogives are fit as logistic regressions to individual fish specimens, which are categorized as mature vs. not mature. The solid black lines represent fits to the female fish and the dashed grey lines represent fits to the male fish. The vertical lines indicate the estimated age or length at 50% maturity. Text on the panels indicates the estimated age and length at 5, 50 and 95% maturity for females (F) and males (M). Model fits are only shown for cases where there are at least 20 mature and 20 immature males and females. Short rug lines along the top and bottom of each panel represent up to 1500 randomly chosen individual fish with a small amount of random jittering in the case of ages to help differentiate individual fish. Models are fit to all available survey samples regardless of time of year. See Appendix H in Anderson et al. (2019) for details.
<!-- `r base_model$dat$start.yr` to `r base_model$dat$end.yr` for `r sp`.  -->

(ref:fig-mat-fr) L’âge-et-la-longueur-à-maturité pour les courbes de fréquences cumulées. Les courbes de fréquences cumulées de maturité sont ajustées en tant que régressions logistiques aux spécimens de poissons individuels, qui sont classés comme étant matures ou non matures. Les lignes noires pleines représentent les ajustements aux poissons femelles et les lignes grises tiretées représentent les ajustements aux poissons mâles. Les lignes verticales indiquent l’âge ou la longueur estimée à 50% de maturité. Le texte sur les panneaux indique l’âge et la longueur estimés à 5, 50 et 95% de maturité pour les femelles (F) et les mâles (M). Les ajustements du modèle ne sont montrés que dans les cas où il y a au moins 20 mâles et 20 femelles matures et 20 mâles et 20 femelles immatures. De courtes lignes le long du haut et du bas de chaque panneau représentent jusqu’à 1 500 poissons individuels choisis au hasard, avec une petite gigue aléatoire dans le cas des âges pour aider à différencier les poissons individuels. Les modèles sont ajustés à tous les échantillons de relevé disponibles, quelle que soit la période de l’année. Voir l'annexe H dans Anderson et al. (2019) pour plus de détails.

```{r fig-mat, fig.cap = ifelse(fr(), "(ref:fig-mat-fr)", "(ref:fig-mat-en)"), fig.asp = 1, out.width = "6in"}

mat_fn <- file.path(data_dir, "fit_mat_ogive_output.rds")
if(file.exists(mat_fn)){
  mat_lst <- readRDS(mat_fn)
}else{
  mat_lst <- list(
    fit_mat_ogive(filter(survey_samples, survey_abbrev %in% "SYN QCS")),
    fit_mat_ogive(filter(survey_samples, survey_abbrev %in% "SYN QCS"), type = "length"),
    fit_mat_ogive(filter(survey_samples, survey_abbrev %in% "SYN HS")),
    fit_mat_ogive(filter(survey_samples, survey_abbrev %in% "SYN HS"), type = "length"),
    fit_mat_ogive(filter(survey_samples, survey_abbrev %in% "SYN WCVI")),
    fit_mat_ogive(filter(survey_samples, survey_abbrev %in% "SYN WCVI"), type = "length"),
    fit_mat_ogive(survey_samples_syn),
    fit_mat_ogive(survey_samples_syn, type = "length"))
  saveRDS(mat_lst, mat_fn)
}
mat_title_lst <- list(
  en2fr("SYN QCS (5AB)", fr()),
  "",
  en2fr("SYN HS (5CD)", fr()),
  "",
  en2fr("SYN WCVI (3CD)", fr()),
  "",
  en2fr("Coastwide synoptic trawl surveys", fr()),
  "")

plot_mat_panels <- function(fit_obj, type = "age"){
  p <- plot_mat_ogive(fit_obj) +
    guides(colour = "none", fill = "none", lty = "none") +
    ggplot2::guides(lty = "none", colour = "none") +
    theme(axis.title.y = element_blank())
  p
}

ma_plot_lst <- list(
  plot_mat_panels(mat_lst[[1]]) +
  theme(axis.title = element_blank()) +
  ggtitle(mat_title_lst[[1]]),

  plot_mat_panels(mat_lst[[2]]) +
  ggtitle(mat_title_lst[[2]]),

  plot_mat_panels(mat_lst[[3]]) +
  theme(axis.title = element_blank()) +
  ggtitle(mat_title_lst[[3]]),

  plot_mat_panels(mat_lst[[4]]) +
  theme(axis.title = element_blank()) +
  ggtitle(mat_title_lst[[4]]),

  plot_mat_panels(mat_lst[[5]]) +
  theme(axis.title = element_blank()) +
  ggtitle(mat_title_lst[[5]]),

  plot_mat_panels(mat_lst[[6]]) +
  theme(axis.title = element_blank()) +
  ggtitle(mat_title_lst[[6]]),

  plot_mat_panels(mat_lst[[7]]) +
  ggtitle(mat_title_lst[[7]]) +
  xlab(en2fr("Age (years)", fr())),

  plot_mat_panels(mat_lst[[8]]) +
  ggtitle(mat_title_lst[[8]]) +
  xlab(paste0(en2fr("Length", fr()), " (cm)")))

grid.arrange(grobs = ma_plot_lst,
             ncol = 2,
             left = paste0(en2fr("Probability mature", fr())))
```

 <!-- Length compositions: --------------------------------------------------------->

(ref:fig-lengths-en) Length-frequency plot where female fish are shown as coloured bars and male fish are shown behind as light grey bars. The total number of fish measured for a given survey and year are indicated in the top left corner of each panel. Histograms are only shown if there are more than 20 fish measured for a given survey-year combination. The commercial male and female fish are combined (black bars) since many are unsexed. 
TODO: describe weighting?

(ref:fig-lengths-fr) Graphique de la fréquence selon la longueur où les poissons femelles sont représentés par des barres colorées et les poissons mâles sont représentés derrière par des barres gris clair. Le nombre total de poissons mesurés pour un relevé et une année donnés est indiqué au coin supérieur gauche de chaque panneau. Les histogrammes ne sont présentés que s’il y a plus de 20 poissons mesurés pour une combinaison donnée de relevé et d’année. Les poissons commerciaux mâles et femelles sont combinés (barres noires), car plusieurs d’entre eux ne sont pas sexués. 
TODO: translate weighting description?

```{r fig-lengths, fig.cap = ifelse(fr(), "(ref:fig-lengths-fr)", "(ref:fig-lengths-en)"), fig.asp = 1, out.width = "6in"}

bin_width1 <- diff(quantile(length_samples_survey$length,
  na.rm = TRUE,
  probs = c(0, 1)
)) / 20

bin_width2 <- diff(quantile(length_samples_ft$length,
  na.rm = TRUE, probs = c(0, 1)
)) / 20

bin_width3 <- diff(quantile(length_samples_ss$length,
  na.rm = TRUE, probs = c(0, 1)
)) / 20

bin_width <- mean(c(bin_width1, bin_width2, bin_width3), na.rm = TRUE)

ss <- tidy_lengths_weighted(length_samples_survey,
  dat_survey_sets = dat$survey_sets,
  bin_size = bin_width,
  sample_type = "survey"
)

sf <- length_samples_ft %>%
  mutate(sex = 2) %>% # fake all sex as female for commercial samples; often not sexed
  tidy_lengths_weighted(
    dat_catch = dat$catch,
    bin_size = bin_width,
    sample_type = "commercial", spp_cat_code = 1
  ) %>%
  mutate(
    survey_abbrev = "Freezer Trawlers"
  )

sc <- length_samples_ss %>%
  mutate(sex = 2) %>% # fake all sex as female for commercial samples; often not sexed
  tidy_lengths_weighted(
    dat_catch = dat$catch,
    bin_size = bin_width,
    sample_type = "commercial", spp_cat_code = 1
  ) %>%
  mutate(
    survey_abbrev = "Shoreside"
  )

min_total <- 20

sc_old <- filter(sc, year < 1995) # are we interested in length frequencies pre-1980?
sc <- filter(sc, year > 1995)
sb <- suppressWarnings(bind_rows(ss, sc, sf))
sb$survey_abbrev <- factor(sb$survey_abbrev,
  levels = c(
    "SYN WCHG", "SYN HS", "SYN QCS", "SYN WCVI",
    en2fr("Freezer Trawlers", fr()), en2fr("Shoreside", fr())
  )
)
sb$year <- factor(sb$year, levels = seq(1996, 2021))

g_lengths <- plot_lengths(sb,
  survey_cols = stats::setNames(
    c("#FC8D62", "#FC8D62", "#FC8D62", "#FC8D62", "#000000", "#000000"),
    c(
      "SYN WCHG", "SYN HS", "SYN QCS", "SYN WCVI",
      en2fr("Freezer Trawlers", fr()),
      en2fr("Shoreside", fr())
    )
  ),
  bin_size = bin_width, min_total = min_total
) +
  # scale_x_continuous(breaks = x_breaks, labels = x_labels) +
  guides(colour = "none", fill = "none") +
  ggtitle("") +
  ggplot2::xlab(paste(en2fr("Length", fr()), "(cm)")) +
  ggplot2::ylab(en2fr("Relative length frequency", fr()))

g_lengths
```
